---
title: "COVID impact on onsultation rate"
author: "YT Y"
date: "25/02/2022"
output: html_document
---

## Negative binomial regression
tutorial. https://stats.oarc.ucla.edu/r/dae/negative-binomial-regression/ 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '/workspace')
```

## Methods 

Interrupted time-series analyses are conducted to compare the difference of consultation rate before and during pandemic. Pre-pandemic period for Covid-19 is defined as 1st January 2019 to 31st December 2019, and the pandemic period is defined as 1st April 2020 to 31st December 2021. Assessment period is defined as every month to acquire the counts of infection consultations and the number of populations. Negative binomial regression model is used to adjust for regions, age categories, month(seasonality), and indecent or prevalent infections for 6 types of infections. 

```{r message=FALSE}
library("ggplot2")
library("data.table")
library("dplyr")
library("tidyverse")
library("MASS")
#library("gtsummary")
```


### Import data

#### 01.  extracted variables from "basic_record_20_"

```{r }

#df19 = read_rds(here("output","measures","basic_record_2019.rds"))
#df19 = read_rds("basic_record_2019.rds")
#df19=df19%>% dplyr::select(practice,region)

df19 = read_rds(here::here("output","measures","basic_record_2019.rds"))
df19=df19%>% dplyr::select(practice,region)

df20 = read_rds(here::here("output","measures","basic_record_2020.rds"))
df20=df20%>% dplyr::select(practice,region)

df21 = read_rds(here::here("output","measures","basic_record_2021.rds"))
df21=df21%>% dplyr::select(practice,region)

region=rbind(df19,df20,df21)
region=region%>%distinct(practice, .keep_all = TRUE)

rm(df19,df20,df21) 
```


#### 02. read measures_uti
```{r}

###1.2 LRTI
#import data 

df <- read_csv(
  here::here("output", "measures", "measure_infection_consult_LRTI.csv"),
  col_types = cols_only(
    
    # Identifier
    practice = col_integer(),
    
    # Outcomes
    lrti_counts  = col_double(), 
    population  = col_double(),
    hx_lrti_pt = col_double(),
    age_cat = col_character(),
    value = col_double(),
    
    # Date
    date = col_date(format="%Y-%m-%d")
    
  ),
  na = character()
)
df$date <- as.Date(df$date)

df=df%>% rename(infection_counts=uti_counts, hx_pt=hx_uti_pt)

df[is.na(df)] <- 0 # replace NA ->0

```

#### 03. add variables
```{r}
# add region variables
df=merge(df,region, by= "practice")
rm(region)

# define covid date
breaks <- c(as.Date("2019-01-01"),as.Date("2019-12-31"),# 1=pre-covid, 2=exclusion
            as.Date("2020-04-01"), as.Date("2021-12-31"),# 3= covid time
            max(df$date)) # NA exclusion

df=df%>%mutate(covid=cut(date,breaks,labels = 1:4))

df=df%>% filter(covid==1 | covid==3)
df$covid= recode(df$covid, '1'="0", '3'="1") # precovid=0, covid=1
df$covid <- factor(df$covid, levels=c("0","1"))

# month for adjust seasonality
df$month=format(df$date,"%m")


# sort age
df$age_cat <- factor(df$age_cat, levels=c("0-4", "5-14","15-24","25-34","35-44","45-54","55-64","65-74","75+"))

```


# Description of data
```{r}

df=df%>%dplyr::select(covid, region, age_cat, month, hx_pt, infection_counts,population)
df$rate=df$infection_counts/df$population*1000

 # tbl_summary(
  #  df,
   # by = covid, # split table by group
 #   missing = "no" # don't list missing data separately
  #) %>%
  #add_n() %>% # add column with total number of non-missing observations
  #modify_header(label = "**Variable**") %>% # update the column header
  #bold_labels() 

```




## Distribution of infection counts
This plot showed the distribution of infection consultation counts by each independent variable.
If discrepancies of distribution are observed, those may be predictors to infection consultation change.

#### covid time

```{r}
ggplot(df, aes(infection_counts, fill =covid )) + 
  geom_histogram(binwidth = 1) + 
  facet_grid(covid~. , margins = TRUE, scales = "free")

```

#### region

```{r}
ggplot(df, aes(infection_counts, fill =region )) + 
  geom_histogram(binwidth = 1) + 
  facet_grid(region~. , margins = TRUE, scales = "free")

```


#### age_cat

```{r}
ggplot(df, aes(infection_counts, fill =age_cat )) + 
  geom_histogram(binwidth = 1) + 
  facet_grid(age_cat~. , margins = TRUE, scales = "free")

```

#### seasonality: month 

```{r}
ggplot(df, aes(infection_counts, fill =month )) + 
  geom_histogram(binwidth = 1) + 
  facet_grid(month~. , margins = TRUE, scales = "free")

```


#### prevalent: with same infection before recent 90 days of index date

```{r}
ggplot(df, aes(infection_counts, fill =hx_pt )) + 
  geom_histogram(binwidth = 1) + 
  facet_grid(hx_pt~. , margins = TRUE, scales = "free")

```





### check over-dispersion
If the variances within each level of independent variables are higher than the means, which suggest data presented over-dispersion, then need to use Negative Binomial model.

output returning mean(SD):

```{r}
# covid time
with(df, tapply(infection_counts, covid, function(x) {
  sprintf("M (SD) = %1.2f (%1.2f)", mean(x), sd(x))
}))

# region
with(df, tapply(infection_counts, region, function(x) {
  sprintf("M (SD) = %1.2f (%1.2f)", mean(x), sd(x))
}))

# age_cat
with(df, tapply(infection_counts, age_cat, function(x) {
  sprintf("M (SD) = %1.2f (%1.2f)", mean(x), sd(x))
}))

# month
with(df, tapply(infection_counts, month, function(x) {
  sprintf("M (SD) = %1.2f (%1.2f)", mean(x), sd(x))
}))

# prevalent
with(df, tapply(infection_counts, hx_pt, function(x) {
  sprintf("M (SD) = %1.2f (%1.2f)", mean(x), sd(x))
}))

```


### Negative binomial regression analysis

##### 01. y=infection counts
```{r}

summary(m1 <- glm.nb(infection_counts~ covid + region + age_cat + month+ hx_pt, data = df))

```

##### 02. y= rate (infection counts/population*1000)
```{r}

#summary(m1.2 <- glm.nb(rate~ covid + region + age_cat + month+ hx_pt, data = df))

```


##### 03. offset

```{r}
#summary(m1.3 <- glm.nb(infection_counts~ offset(log(population))+ covid + region + age_cat + month+ hx_pt, data = df))

#summary(m1.3 <- glm(infection_counts~offset(log(population)) + covid + region + age_cat + month+ hx_pt, family=negative.binomial(m1$theta), data = df))

```

### compare models without covid time variable
Since covid time is considered as the most important variables of interest, so we can compare two models with and without covid time to determine if itself significant.
If the chi-square test is significant, this indicates that covid time is a statistically significant predictor of infection counts.
```{r}
m2 <- update(m1, . ~ . - covid)
anova(m1, m2)
```


