---
title: "COVID impact on broad_spectrum prescribing proportion"
author: "Billy Z"
date: "28/02/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '/workspace')
```

## Methods 

The pre-pandemic period for Covid-19 is defined as 1st January 2019 to 31st December 2019, and the pandemic period is defined as 1st April 2020 to 31st December 2021. Logistic regression model one is used to adjust for age categories, sex. The second logistic regression model was used as a fully adjusted model to adjust for age categories, sex, Charlson Comorbidity score, socioeconomic status, ethnicity, flu vaccination, antibiotics prescription record in 12 months before, hospitalisation in the previous year, Season of consultation, month(seasonality), and incident or prevalent infections for 6 types of infections. 


```{r message=FALSE}
library("ggplot2")
library("data.table")
library("dplyr")
library("tidyverse")
```

### Import data

#### 01.  extracted variables from "model_variable_broad_2019_"

```{r}

df19_1 = read_rds(here::here("output","measures","model_variable_broad_2019_1.rds"))
df19_1=df19_1%>% dplyr::select( date, patient_id, practice, age_cat,
                            ethnicity_6, flu_vaccine, imd, antibacterial_12mb4, gp_count)

df19_2 = read_rds(here::here("output","measures","model_variable_broad_2019_2.rds"))
df19_2=df19_2%>% dplyr::select(charlson_score,patient_id,date)

df19_ab = read_rds(here::here("output","measures","recorded_ab_broad_2019.rds"))
df19_ab=dplyr::bind_rows(df19_ab)

# recode empty value
df19_ab$infection=ifelse(df19_ab$infection=="","uncoded",df19_ab$infection)
df19_ab$infection=df19_ab$infection %>% replace_na("uncoded")
  
# recode
df19_ab$infection=recode(df19_ab$infection,
                       asthma ="Other_infection",
                       cold="Other_infection",
                       cough="Other_infection",
                       copd="Other_infection",
                       pneumonia="Other_infection",
                       renal="Other_infection",
                       sepsis="Other_infection",
                       throat="Other_infection",
                       uti = "UTI",
                       lrti = "LRTI",
                       urti = "URTI",
                       sinusits = "Sinusitis",
                       otmedia = "Otitis_media",
                       ot_externa = "Otitis_externa",
                       uncoded = "Uncoded")
  
# recode empty value
df19_ab$infection=ifelse(df19_ab$infection=="","uncoded",df19_ab$infection)

df <- merge(df19_ab,df19_2,by=c('patient_id','date'))
rm(df19_ab,df19_2)
df <- merge(df,df19_1,by=c('patient_id','date'))
rm(df19_1)

# sort age
df$age_cat <- factor(df$age_cat, levels=c("0-4", "5-14","15-24","25-34","35-44","45-54","55-64","65-74","75+"))
df$infection <- factor(df$infection, levels=c("LRTI","Otitis_externa","Otitis_media","Sinusitis","URTI","UTI","Other_infection","Uncoded"))

```

# Description of data
```{r echo=FALSE}
df_broad <- df %>% select(patient_id, date, prevalent, infection, broad_spectrum, practice, age_cat, sex)
df_broad_count <- df_broad %>%filter(broad_spectrum==1) %>%  group_by(date,prevalent) %>% summarise(count=n())
df_broad_count$prevalent=recode(df_broad_count$prevalent,
                       "1" ="prevalent",
                       "0" = "incident")
# Plot
df_broad_count %>%
  ggplot( aes(x=date, y=count, group=prevalent, color=prevalent)) +
    geom_line() +
    ggtitle("Broad-spectrum antibiotics prescription changes in time") +
    ylab("Broad-spectrum antibiotics prescription")

```


### Logistic regression analysis
model 1
```{r}
m1 <- glm(broad_spectrum ~ age_cat + sex, family = binomial(link = "logit"),data = df_broad)
summary(m1)
```
### Logistic regression analysis
model 2
```{r}
df$month=format(df$date,"%m")
df=df%>% mutate(season= case_when( month=="03"|month=="04"|month=="05" ~ "spring",
                                   month=="06"|month=="07"|month=="08" ~ "summer",
                                   month=="09"|month=="10"|month=="11" ~ "autumn",
                                   month=="12"|month=="01"|month=="02" ~ "winter"))


m2 <- glm (broad_spectrum ~ as.factor(season) + age_cat + sex + as.factor(prevalent) + infection + 
               charlson_score + ethnicity_6 + flu_vaccine + imd + gp_count +antibacterial_12mb4, family = binomial(link = "logit"),data = df)
summary(m2)
```


