---
title: "Indicent consultation rate - ITS, cat_month"
output: 
  html_document:
   toc: true
   toc_depth: 2
   toc_float:
     collapsed: false
     smooth_scorll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir = '/workspace')
```

## Interrupted time-series analysis

```{r message=FALSE}
library("ggplot2")
library("data.table")
library("dplyr")
library("tidyverse")
library("MASS")
#library("gtsummary")
```

```{r message=FALSE}

# import incident cases
df = read_csv(here::here("output","redacted","consultation_rate_incident_check.csv"))

# define covid date
breaks <- c(as.Date("2019-01-01"),as.Date("2019-12-31"),# 1=pre-covid, 2=exclusion
            as.Date("2020-04-01"), as.Date("2021-12-31"),# 3= covid time
            max(df$date)) # NA exclusion

df=df%>%mutate(covid=cut(date,breaks,labels = 1:4))

df=df%>% filter(covid==1 | covid==3)
df$covid= recode(df$covid, '1'="0", '3'="1") # precovid=0, covid=1
df$covid <- factor(df$covid, levels=c("0","1"))


# infection counts, population size, covid period
df= df%>% group_by(date, covid,indic)%>% 
  summarise(counts=sum(counts), 
            population=sum(population))

# month for adjust seasonality
df$month=format(df$date,"%m")
df=df%>% mutate(season= case_when( month=="03"|month=="04"|month=="05" ~ "spring",
                                   month=="06"|month=="07"|month=="08" ~ "summer",
                                   month=="09"|month=="10"|month=="11" ~ "autumn",
                                   month=="12"|month=="01"|month=="02" ~ "winter"))
df$month=df$season

# time elapsed(measurement time point) for linear effect of time to capture long-term behaviour trends
df$times <- as.numeric(as.factor(df$date))

# time sequnece after covid
df=df%>% group_by(covid)%>%mutate(time.since=1:n())
df$time.since <- ifelse(df$covid==0,0,df$time.since)


df1=df%>%filter(indic=="UTI")
df2=df%>%filter(indic=="LRTI")
df3=df%>%filter(indic=="URTI") 
df4=df%>%filter(indic=="sinusitis")
df5=df%>%filter(indic=="otitis externa")
df6=df%>%filter(indic=="otitis media")


```



# model1: without month

##UTI
```{r}
summary(m1 <- glm.nb(counts~ offset(log(population))+ covid + time.since +times , data = df1))
```

## URTI
```{r}
summary(m2 <- glm.nb(counts~ offset(log(population))+ covid + time.since +times , data = df2))
```

## LRTI
```{r}
summary(m3 <- glm.nb(counts~ offset(log(population))+ covid + time.since +times , data = df3))
```

## Sinusitis
```{r}
summary(m4 <- glm.nb(counts~ offset(log(population))+ covid + time.since +times , data = df4))
```

## otitis externa
```{r}
summary(m5 <- glm.nb(counts~ offset(log(population))+ covid + time.since +times , data = df5))
```

## otitis media
```{r}
summary(m6 <- glm.nb(counts~ offset(log(population))+ covid + time.since +times , data = df6))
```


```{r message=FALSE, include=FALSE}
### confidence intervals for the coefficients
(est1 <- cbind(Estimate = coef(m1), confint(m1)))
(est2 <- cbind(Estimate = coef(m2), confint(m2)))
(est3 <- cbind(Estimate = coef(m3), confint(m3)))
(est4 <- cbind(Estimate = coef(m4), confint(m4)))
(est5 <- cbind(Estimate = coef(m5), confint(m5)))
(est6 <- cbind(Estimate = coef(m6), confint(m6)))

```


```{r message=FALSE}
### calculate IRR & 95%CI
est1=exp(est1)
est2=exp(est2)
est3=exp(est3)
est4=exp(est4)
est5=exp(est5)
est6=exp(est6)
```


```{r message=FALSE}
#### combined results
DF=bind_rows(est1[2,],est2[2,],est3[2,],est4[2,],est5[2,],est6[2,])

DF$Infection=c("UTI","URTI","LRTI","Sinusitis","Otitis externa","Otitis media")
#reorder
DF=DF%>%arrange(Infection)

names(DF)[1]="IRR"
names(DF)[2]="ci_l"
names(DF)[3]="ci_u"
DF
```



```{r message=FALSE}
### result_model1
#setting up the basic plot
p1 <- ggplot(data=DF, aes(y=Infection, x=IRR, xmin=ci_l, xmax=ci_u))+ 

#this adds the effect sizes to the plot
geom_point()+ 

#adds the CIs
geom_errorbarh(height=.1)+

#adding a vertical line at the effect = 0 mark
geom_vline(xintercept=1, color="black", linetype="dashed", alpha=.5)+
  
#thematic stuff
theme_minimal()+
theme(text=element_text(family="Times",size=18, color="black"))+
theme(panel.spacing = unit(1, "lines"))+

labs(
    title = "Consultation Reduction",
    x="IRR (95% CI)"
  )

```




# model2:add month

## UTI
```{r}
summary(m1.1 <- glm.nb(counts~ offset(log(population))+ covid + month + times + time.since  , data = df1))
```

## URTI
```{r}
summary(m2.1 <- glm.nb(counts~ offset(log(population))+ covid + month + times + time.since  , data = df2))
```

## LRTI
```{r}
summary(m3.1 <- glm.nb(counts~ offset(log(population))+ covid + month + times + time.since , data = df3))
```

## sinusitis
```{r}
summary(m4.1 <- glm.nb(counts~ offset(log(population))+ covid + month + times + time.since  , data = df4))
```

## otitis externa
```{r}
summary(m5.1 <-glm.nb(counts~ offset(log(population))+ covid + month + times + time.since , data = df5))
```

## otitis media
```{r }
summary(m6.1 <- glm.nb(counts~ offset(log(population))+ covid + month + times + time.since  , data = df6))
```


```{r message=FALSE, include=FALSE}
### confidence intervals for the coefficients
(est1.1 <- cbind(Estimate = coef(m1.1), confint(m1.1)))
(est2.1 <- cbind(Estimate = coef(m2.1), confint(m2.1)))
(est3.1 <- cbind(Estimate = coef(m3.1), confint(m3.1)))
(est4.1 <- cbind(Estimate = coef(m4.1), confint(m4.1)))
(est5.1 <- cbind(Estimate = coef(m5.1), confint(m5.1)))
(est6.1 <- cbind(Estimate = coef(m6.1), confint(m6.1)))

```


```{r message=FALSE}
### calculate IRR & 95%CI
est1.1=exp(est1.1)
est2.1=exp(est2.1)
est3.1=exp(est3.1)
est4.1=exp(est4.1)
est5.1=exp(est5.1)
est6.1=exp(est6.1)
```

### covid
```{r message=FALSE}
## combine results
# covid
DF=bind_rows(est1.1[2,],est2.1[2,],est3.1[2,],est4.1[2,],est5.1[2,],est6.1[2,])
DF$Infection=c("UTI","URTI","LRTI","Sinusitis","Otitis externa","Otitis media")
#reorder
DF=DF%>%arrange(Infection)

names(DF)[1]="IRR"
names(DF)[2]="ci_l"
names(DF)[3]="ci_u"

DF
```




```{r message=FALSE}
### Model2_result
#setting up the basic plot
p2 <- ggplot(data=DF, aes(y=Infection, x=IRR, xmin=ci_l, xmax=ci_u))+ 

#this adds the effect sizes to the plot
geom_point()+ 

#adds the CIs
geom_errorbarh(height=.1)+

#adding a vertical line at the effect = 0 mark
geom_vline(xintercept=1, color="black", linetype="dashed", alpha=.5)+
  
#thematic stuff
theme_minimal()+
theme(text=element_text(family="Times",size=18, color="black"))+
theme(panel.spacing = unit(1, "lines"))+

labs(
      title = "Consultation Reduction",
    x="IRR (95% CI)"
  )
```

# comparing results
### level change
## model1: without month
```{r}
p1
```

## model2: add month
```{r}
p2
```



## comparing models

##UTI
### model 1 vs. model2 (with or without interaction)
```{r}
anova(m1,m1.1)

```


## URTI
### model 1 vs. model2 (with or without interaction)
```{r}
anova(m2,m2.1)

```


## LRTI
### model 1 vs. model2 (with or without interaction)
```{r}
anova(m3,m3.1)

```


## sinusitis
### model 1 vs. model2 (with or without interaction)
```{r}
anova(m4,m4.1)

```


## otitis externa
### model 1 vs. model2 (with or without interaction)
```{r}
anova(m5,m5.1)

```


## otitis media
### model 1 vs. model2 (with or without interaction)
```{r}
anova(m6,m6.1)

```


# Model checking and autocorrelation
## model 1
### UTI
```{r}
#b) 
# Check the residuals by plotting against time
res1 <- residuals(m1,type="deviance")
plot(df1$date,res1,ylim=c(-5,10),pch=19,cex=0.7,col=grey(0.6),
     main="Residuals over time",ylab="Deviance residuals",xlab="Date")
abline(h=0,lty=2,lwd=2)

# Further check for autocorrelation by examining the autocorrelation and
#   partial autocorrelation functions
acf(res1)
pacf(res1)
Box.test(res1, lag=32, type="Ljung-Box")
rm(res1)
```

### LRTI
```{r}
#b) 
# Check the residuals by plotting against time
res2 <- residuals(m2,type="deviance")
plot(df2$date,res2,ylim=c(-5,10),pch=19,cex=0.7,col=grey(0.6),
     main="Residuals over time",ylab="Deviance residuals",xlab="Date")
abline(h=0,lty=2,lwd=2)

# Further check for autocorrelation by examining the autocorrelation and
#   partial autocorrelation functions
acf(res2)
pacf(res2)
Box.test(res2, lag=32, type="Ljung-Box")
rm(res2)
```

### URTI
```{r}
#b) 
# Check the residuals by plotting against time
res3 <- residuals(m3,type="deviance")
plot(df3$date,res3,ylim=c(-5,10),pch=19,cex=0.7,col=grey(0.6),
     main="Residuals over time",ylab="Deviance residuals",xlab="Date")
abline(h=0,lty=2,lwd=2)

# Further check for autocorrelation by examining the autocorrelation and
#   partial autocorrelation functions
acf(res3)
pacf(res3)
Box.test(res3, lag=32, type="Ljung-Box")
rm(res3)
```

### Sinusitis
```{r}
#b) 
# Check the residuals by plotting against time
res4 <- residuals(m4,type="deviance")
plot(df4$date,res4,ylim=c(-5,10),pch=19,cex=0.7,col=grey(0.6),
     main="Residuals over time",ylab="Deviance residuals",xlab="Date")
abline(h=0,lty=2,lwd=2)

# Further check for autocorrelation by examining the autocorrelation and
#   partial autocorrelation functions
acf(res4)
pacf(res4)
Box.test(res4, lag=32, type="Ljung-Box")
rm(res4)
```


### Otitis externa
```{r}
#b) 
# Check the residuals by plotting against time
res5 <- residuals(m5,type="deviance")
plot(df5$date,res5,ylim=c(-5,10),pch=19,cex=0.7,col=grey(0.6),
     main="Residuals over time",ylab="Deviance residuals",xlab="Date")
abline(h=0,lty=2,lwd=2)

# Further check for autocorrelation by examining the autocorrelation and
#   partial autocorrelation functions
acf(res5)
pacf(res5)
Box.test(res5, lag=32, type="Ljung-Box")
rm(res5)
```

### Otitis media
```{r}
#b) 
# Check the residuals by plotting against time
res6 <- residuals(m6,type="deviance")
plot(df6$date,res6,ylim=c(-5,10),pch=19,cex=0.7,col=grey(0.6),
     main="Residuals over time",ylab="Deviance residuals",xlab="Date")
abline(h=0,lty=2,lwd=2)

# Further check for autocorrelation by examining the autocorrelation and
#   partial autocorrelation functions
acf(res6)
pacf(res6)
Box.test(res6, lag=32, type="Ljung-Box")
rm(res6)
```


## model 2
### UTI
```{r}
#b) 
# Check the residuals by plotting against time
res1 <- residuals(m1.1,type="deviance")
plot(df1$date,res1,ylim=c(-5,10),pch=19,cex=0.7,col=grey(0.6),
     main="Residuals over time",ylab="Deviance residuals",xlab="Date")
abline(h=0,lty=2,lwd=2)

# Further check for autocorrelation by examining the autocorrelation and
#   partial autocorrelation functions
acf(res1)
pacf(res1)

acf(res1,lag.max=32)
pacf(res1,lag.max=32)

Box.test(res1, lag=32, type="Ljung-Box")
rm(res1)
```

### LRTI
```{r}
#b) 
# Check the residuals by plotting against time
res2 <- residuals(m2.1,type="deviance")
plot(df2$date,res2,ylim=c(-5,10),pch=19,cex=0.7,col=grey(0.6),
     main="Residuals over time",ylab="Deviance residuals",xlab="Date")
abline(h=0,lty=2,lwd=2)

# Further check for autocorrelation by examining the autocorrelation and
#   partial autocorrelation functions
acf(res2)
pacf(res2)

acf(res2,lag.max=32)
pacf(res2,lag.max=32)

Box.test(res2, lag=32, type="Ljung-Box")
rm(res2)
```

### URTI
```{r}
#b) 
# Check the residuals by plotting against time
res3 <- residuals(m3.1,type="deviance")
plot(df3$date,res3,ylim=c(-5,10),pch=19,cex=0.7,col=grey(0.6),
     main="Residuals over time",ylab="Deviance residuals",xlab="Date")
abline(h=0,lty=2,lwd=2)

# Further check for autocorrelation by examining the autocorrelation and
#   partial autocorrelation functions
acf(res3)
pacf(res3)

acf(res3,lag.max=32)
pacf(res3,lag.max=32)

Box.test(res3, lag=32, type="Ljung-Box")
rm(res3)
```

### Sinusitis
```{r}
#b) 
# Check the residuals by plotting against time
res4 <- residuals(m4.1,type="deviance")
plot(df4$date,res4,ylim=c(-5,10),pch=19,cex=0.7,col=grey(0.6),
     main="Residuals over time",ylab="Deviance residuals",xlab="Date")
abline(h=0,lty=2,lwd=2)

# Further check for autocorrelation by examining the autocorrelation and
#   partial autocorrelation functions
acf(res4)
pacf(res4)

acf(res4,lag.max=32)
pacf(res4,lag.max=32)
Box.test(res4, lag=32, type="Ljung-Box")
rm(res4)
```


### Otitis externa
```{r}
#b) 
# Check the residuals by plotting against time
res5 <- residuals(m5.1,type="deviance")
plot(df5$date,res5,ylim=c(-5,10),pch=19,cex=0.7,col=grey(0.6),
     main="Residuals over time",ylab="Deviance residuals",xlab="Date")
abline(h=0,lty=2,lwd=2)

# Further check for autocorrelation by examining the autocorrelation and
#   partial autocorrelation functions
acf(res5)
pacf(res5)

acf(res5,lag.max=32)
pacf(res5,lag.max=32)
Box.test(res5, lag=32, type="Ljung-Box")
rm(res5)
```

### Otitis media
```{r}
#b) 
# Check the residuals by plotting against time
res6 <- residuals(m6.1,type="deviance")
plot(df6$date,res6,ylim=c(-5,10),pch=19,cex=0.7,col=grey(0.6),
     main="Residuals over time",ylab="Deviance residuals",xlab="Date")
abline(h=0,lty=2,lwd=2)

# Further check for autocorrelation by examining the autocorrelation and
#   partial autocorrelation functions
acf(res6)
pacf(res6)


acf(res6,lag.max=32)
pacf(res6,lag.max=32)

Box.test(res6, lag=32, type="Ljung-Box")
rm(res6)
```


