---
title: "COVID impact on onsultation rate"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir = '/workspace')
```

## Interrupted time-series analysis

```{r message=FALSE}
library("ggplot2")
library("data.table")
library("dplyr")
library("tidyverse")
library("MASS")
#library("gtsummary")
```

```{r message=FALSE}
### Import data
filelist=c("consult_UTI.rds","consult_URTI.rds","consult_LRTI.rds","consult_sinusitis.rds","consult_ot_externa.rds","consult_otmedia.rds")

#temp <- vector("list", length(filelist))

#for (i in seq_along(filelist)){

df = read_rds(here::here("output","measures",filelist[1]))
# infection counts, population size, covid period
df = df%>% group_by(date, covid)%>% 
  summarise(counts=sum(infection_counts), 
            population=sum(population))
# month for seasonality
df$month= format(df$date,"%m")
# time elapsed(measurement time point) for linear effect of time to capture long-term behaviour trends
df$times <- as.numeric(as.factor(df$date))

#temp[[i]]=df

df1=df
rm(df)
#}

df = read_rds(here::here("output","measures",filelist[2]))
# infection counts, population size, covid period
df = df%>% group_by(date, covid)%>% 
  summarise(counts=sum(infection_counts), 
            population=sum(population))
# month for seasonality
df$month= format(df$date,"%m")
# time elapsed(measurement time point) for linear effect of time to capture long-term behaviour trends
df$times <- as.numeric(as.factor(df$date))

#temp[[i]]=df

df2=df
rm(df)

df = read_rds(here::here("output","measures",filelist[3]))
# infection counts, population size, covid period
df = df%>% group_by(date, covid)%>% 
  summarise(counts=sum(infection_counts), 
            population=sum(population))
# month for seasonality
df$month= format(df$date,"%m")
# time elapsed(measurement time point) for linear effect of time to capture long-term behaviour trends
df$times <- as.numeric(as.factor(df$date))

#temp[[i]]=df

df3=df
rm(df)

df = read_rds(here::here("output","measures",filelist[4]))
# infection counts, population size, covid period
df = df%>% group_by(date, covid)%>% 
  summarise(counts=sum(infection_counts), 
            population=sum(population))
# month for seasonality
df$month= format(df$date,"%m")
# time elapsed(measurement time point) for linear effect of time to capture long-term behaviour trends
df$times <- as.numeric(as.factor(df$date))

#temp[[i]]=df

df4=df
rm(df)


df = read_rds(here::here("output","measures",filelist[5]))
# infection counts, population size, covid period
df = df%>% group_by(date, covid)%>% 
  summarise(counts=sum(infection_counts), 
            population=sum(population))
# month for seasonality
df$month= format(df$date,"%m")
# time elapsed(measurement time point) for linear effect of time to capture long-term behaviour trends
df$times <- as.numeric(as.factor(df$date))

#temp[[i]]=df

df5=df
rm(df)


df = read_rds(here::here("output","measures",filelist[6]))
# infection counts, population size, covid period
df = df%>% group_by(date, covid)%>% 
  summarise(counts=sum(infection_counts), 
            population=sum(population))
# month for seasonality
df$month= format(df$date,"%m")
# time elapsed(measurement time point) for linear effect of time to capture long-term behaviour trends
df$times <- as.numeric(as.factor(df$date))

#temp[[i]]=df

df6=df
rm(df)

```

```{r message=FALSE}
#df1=temp[[1]]#uti
#df2=temp[[2]]#urti
#df3=temp[[3]]#lrti
#df4=temp[[4]]#sinusitis
#df5=temp[[5]]#otitis externa
#df6=temp[[6]]#otitis media
#rm(temp)
```


# Negative binomial model (without interaction)_model1

##UTI
```{r}
summary(m1 <- glm.nb(counts~ offset(log(population))+ covid + month +times , data = df1))
```

## URTI
```{r}
summary(m2 <- glm.nb(counts~ offset(log(population))+ covid + month +times , data = df2))
```

## LRTI
```{r}
summary(m3 <- glm.nb(counts~ offset(log(population))+ covid + month +times , data = df3))
```

## Sinusitis
```{r}
summary(m4 <- glm.nb(counts~ offset(log(population))+ covid + month +times , data = df4))
```

## otitis externa
```{r}
summary(m5 <- glm.nb(counts~ offset(log(population))+ covid + month +times , data = df5))

```

## otitis media
```{r}
summary(m6 <- glm.nb(counts~ offset(log(population))+ covid + month +times , data = df6))
```


```{r include=FALSE}
### confidence intervals for the coefficients
(est1 <- cbind(Estimate = coef(m1), confint(m1)))
(est2 <- cbind(Estimate = coef(m2), confint(m2)))
(est3 <- cbind(Estimate = coef(m3), confint(m3)))
(est4 <- cbind(Estimate = coef(m4), confint(m4)))
(est5 <- cbind(Estimate = coef(m5), confint(m5)))
(est6 <- cbind(Estimate = coef(m6), confint(m6)))

```

### calculate IRR & 95%CI
```{r}
est1=exp(est1)
est1=exp(est2)
est1=exp(est3)
est1=exp(est4)
est1=exp(est5)
est1=exp(est6)
```


```{r}
#### combined results
DF=bind_rows(est1[2,],est2[2,],est3[2,],est4[2,],est5[2,],est6[2,])

DF$Infection=c("UTI","URTI","LRTI","Sinusitis","Otitis externa","Otitis media")
#reorder
DF=DF%>%arrange(Infection)

names(DF)[1]="IRR"
names(DF)[2]="ci_l"
names(DF)[3]="ci_u"
DF
```



```{r}
### result_model1
#setting up the basic plot
p1 <- ggplot(data=DF, aes(y=Infection, x=IRR, xmin=ci_l, xmax=ci_u))+ 

#this adds the effect sizes to the plot
geom_point()+ 

#adds the CIs
geom_errorbarh(height=.1)+

#adding a vertical line at the effect = 0 mark
geom_vline(xintercept=0, color="black", linetype="dashed", alpha=.5)+
  
#thematic stuff
theme_minimal()+
theme(text=element_text(family="Times",size=18, color="black"))+
theme(panel.spacing = unit(1, "lines"))+

labs(
    title = "Consultation Reduction",
    x="IRR (95% CI)"
  )

```




# Negative binomial model (adding interaction)_model2

## UTI
```{r}
summary(m1.1 <- glm.nb(counts~ offset(log(population))+ covid + month + times + times*covid  , data = df1))
```

## URTI
```{r}
summary(m2.1 <- glm.nb(counts~ offset(log(population))+ covid + month + times + times*covid  , data = df2))
```

## LRTI
```{r}
summary(m3.1 <- glm.nb(counts~ offset(log(population))+ covid + month + times + times*covid  , data = df3))
```

## sinusitis
```{r}
summary(m4.1 <- glm.nb(counts~ offset(log(population))+ covid + month + times + times*covid  , data = df4))
```

## otitis externa
```{r}
summary(m5.1 <-glm.nb(counts~ offset(log(population))+ covid + month + times + times*covid  , data = df5))
```

## otitis media
```{r }
summary(m6.1 <- glm.nb(counts~ offset(log(population))+ covid + month + times + times*covid  , data = df6))
```


```{r include=FALSE}
### confidence intervals for the coefficients
(est1.1 <- cbind(Estimate = coef(m1.1), confint(m1.1)))
(est2.1 <- cbind(Estimate = coef(m2.1), confint(m2.1)))
(est3.1 <- cbind(Estimate = coef(m3.1), confint(m3.1)))
(est4.1 <- cbind(Estimate = coef(m4.1), confint(m4.1)))
(est5.1 <- cbind(Estimate = coef(m5.1), confint(m5.1)))
(est6.1 <- cbind(Estimate = coef(m6.1), confint(m6.1)))

```

### calculate IRR & 95%CI
```{r}
est1.1=exp(est1.1)
est1.1=exp(est2.1)
est1.1=exp(est3.1)
est1.1=exp(est4.1)
est1.1=exp(est5.1)
est1.1=exp(est6.1)
```


```{r}
## combine results
DF=bind_rows(est1.1[2,],est2.1[2,],est3.1[2,],est4.1[2,],est5.1[2,],est6.1[2,])
DF$Infection=c("UTI","URTI","LRTI","Sinusitis","Otitis externa","Otitis media")
#reorder
DF=DF%>%arrange(Infection)

names(DF)[1]="IRR"
names(DF)[2]="ci_l"
names(DF)[3]="ci_u"
DF
```



```{r}
### Model2_result
#setting up the basic plot
p2 <- ggplot(data=DF, aes(y=Infection, x=IRR, xmin=ci_l, xmax=ci_u))+ 

#this adds the effect sizes to the plot
geom_point()+ 

#adds the CIs
geom_errorbarh(height=.1)+

#adding a vertical line at the effect = 0 mark
geom_vline(xintercept=1, color="black", linetype="dashed", alpha=.5)+
  
#thematic stuff
theme_minimal()+
theme(text=element_text(family="Times",size=18, color="black"))+
theme(panel.spacing = unit(1, "lines"))+

labs(
      title = "Consultation Reduction",
    x="IRR (95% CI)"
  )
```

```{r}

```


# Negative binomial model (adding interaction)_model3

```{r include=FALSE}

df1$residuals=m1.1$residuals
df2$residuals=m2.1$residuals
df3$residuals=m3.1$residuals
df4$residuals=m4.1$residuals
df5$residuals=m5.1$residuals
df6$residuals=m6.1$residuals

rm(m2.1,m3.1,m4.1,m1.1,m5.1,m6.1)

m1.2 <- glm.nb(counts~ offset(log(population))+ covid + month + times + times*covid + residuals , data = df1)
m2.2 <- glm.nb(counts~ offset(log(population))+ covid + month + times + times*covid + residuals , data = df2)
m3.2 <- glm.nb(counts~ offset(log(population))+ covid + month + times + times*covid + residuals , data = df3)
m4.2 <- glm.nb(counts~ offset(log(population))+ covid + month + times + times*covid + residuals , data = df4)
m5.2 <- glm.nb(counts~ offset(log(population))+ covid + month + times + times*covid + residuals , data = df5)
m6.2 <- glm.nb(counts~ offset(log(population))+ covid + month + times + times*covid + residuals , data = df6)

#m2.2=update(m2, .~.  +times*covid +m2.1$residuals)
#m3.2=update(m3, .~.  +times*covid +m3.1$residuals)
#m4.2=update(m4, .~.  +times*covid +m4.1$residuals)
#m5.2=update(m5, .~.  +times*covid +m5.1$residuals)
#m6.2=update(m6, .~.  +times*covid +m6.1$residuals)
```



```{r message=FALSE}
### confidence intervals for the coefficients
(est1.2 <- cbind(Estimate = coef(m1.2), confint(m1.2)))
(est2.2 <- cbind(Estimate = coef(m2.2), confint(m2.2)))
(est3.2 <- cbind(Estimate = coef(m3.2), confint(m3.2)))
(est4.2 <- cbind(Estimate = coef(m4.2), confint(m4.2)))
(est5.2 <- cbind(Estimate = coef(m5.2), confint(m5.2)))
(est6.2 <- cbind(Estimate = coef(m6.2), confint(m6.2)))

```

### calculate IRR & 95%CI
```{r}
est1.2=exp(est1.2)
est1.2=exp(est2.2)
est1.2=exp(est3.2)
est1.2=exp(est4.2)
est1.2=exp(est5.2)
est1.2=exp(est6.2)
```


```{r}
## combine results
DF=bind_rows(est1.2[2,],est2.2[2,],est3.2[2,],est4.2[2,],est5.2[2,],est6.2[2,])

DF$Infection=c("UTI","URTI","LRTI","Sinusitis","Otitis externa","Otitis media")
#reorder
DF=DF%>%arrange(Infection)

names(DF)[1]="IRR"
names(DF)[2]="ci_l"
names(DF)[3]="ci_u"
DF
```



```{r}
### result_model3
#setting up the basic plot
p3 <- ggplot(data=DF, aes(y=Infection, x=IRR, xmin=ci_l, xmax=ci_u))+ 

#this adds the effect sizes to the plot
geom_point()+ 

#adds the CIs
geom_errorbarh(height=.1)+

#adding a vertical line at the effect = 0 mark
geom_vline(xintercept=1, color="black", linetype="dashed", alpha=.5)+
  
#thematic stuff
theme_minimal()+
theme(text=element_text(family="Times",size=18, color="black"))+
theme(panel.spacing = unit(1, "lines"))+

labs( title = "Consultation Reduction",
    x="IRR (95% CI)"
  )

```


# comparing results
## model_1 without interaction
```{r}
p1
```

## model_2 add interaction
```{r}
p2
```

## model_3
```{r}
p3
```

## comparing models

##UTI
### model 1 vs. model2 (with or without interaction)
```{r}
anova(m1,m1.1)

```

### model2 vs. model3 (with or without residuals)
```{r}
anova(m1.1,m1.2)
```

## URTI
### model 1 vs. model2 (with or without interaction)
```{r}
anova(m2,m2.1)

```

### model2 vs. model3 (with or without residuals)
```{r}
anova(m2.1,m2.2)
```

## LRTI
### model 1 vs. model2 (with or without interaction)
```{r}
anova(m3,m3.1)

```

### model2 vs. model3 (with or without residuals)
```{r}
anova(m3.1,m3.2)
```


## sinusitis
### model 1 vs. model2 (with or without interaction)
```{r}
anova(m4,m4.1)

```

### model2 vs. model3 (with or without residuals)
```{r}
anova(m4.1,m4.2)
```


## otitis externa
### model 1 vs. model2 (with or without interaction)
```{r}
anova(m5,m5.1)

```

### model2 vs. model3 (with or without residuals)
```{r}
anova(m5.1,m5.2)
```


## otitis media
### model 1 vs. model2 (with or without interaction)
```{r}
anova(m6,m6.1)

```

### model2 vs. model3 (with or without residuals)
```{r}
anova(m6.1,m6.2)
```
