---
title: "consultation rate - ITS model"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir = '/workspace')
```

## Interrupted time-series analysis

```{r message=FALSE}
library("ggplot2")
library("data.table")
library("dplyr")
library("tidyverse")
library("MASS")
#library("gtsummary")
```

```{r message=FALSE}
### Import data
filelist=c("consult_UTI.rds","consult_URTI.rds","consult_LRTI.rds","consult_sinusitis.rds","consult_ot_externa.rds","consult_otmedia.rds")

#temp <- vector("list", length(filelist))

#for (i in seq_along(filelist)){

df = read_rds(here::here("output","measures",filelist[1]))
# infection counts, population size, covid period
df = df%>% group_by(date, covid)%>% 
  summarise(counts=sum(infection_counts), 
            population=sum(population))
# month for seasonality
df$month= format(df$date,"%m")
# time elapsed(measurement time point) for linear effect of time to capture long-term behaviour trends
df$times <- as.numeric(as.factor(df$date))

#temp[[i]]=df

df1=df
rm(df)
#}

df = read_rds(here::here("output","measures",filelist[2]))
# infection counts, population size, covid period
df = df%>% group_by(date, covid)%>% 
  summarise(counts=sum(infection_counts), 
            population=sum(population))
# month for seasonality
df$month= format(df$date,"%m")
# time elapsed(measurement time point) for linear effect of time to capture long-term behaviour trends
df$times <- as.numeric(as.factor(df$date))

#temp[[i]]=df

df2=df
rm(df)

df = read_rds(here::here("output","measures",filelist[3]))
# infection counts, population size, covid period
df = df%>% group_by(date, covid)%>% 
  summarise(counts=sum(infection_counts), 
            population=sum(population))
# month for seasonality
df$month= format(df$date,"%m")
# time elapsed(measurement time point) for linear effect of time to capture long-term behaviour trends
df$times <- as.numeric(as.factor(df$date))

#temp[[i]]=df

df3=df
rm(df)

df = read_rds(here::here("output","measures",filelist[4]))
# infection counts, population size, covid period
df = df%>% group_by(date, covid)%>% 
  summarise(counts=sum(infection_counts), 
            population=sum(population))
# month for seasonality
df$month= format(df$date,"%m")
# time elapsed(measurement time point) for linear effect of time to capture long-term behaviour trends
df$times <- as.numeric(as.factor(df$date))

#temp[[i]]=df

df4=df
rm(df)


df = read_rds(here::here("output","measures",filelist[5]))
# infection counts, population size, covid period
df = df%>% group_by(date, covid)%>% 
  summarise(counts=sum(infection_counts), 
            population=sum(population))
# month for seasonality
df$month= format(df$date,"%m")
# time elapsed(measurement time point) for linear effect of time to capture long-term behaviour trends
df$times <- as.numeric(as.factor(df$date))

#temp[[i]]=df

df5=df
rm(df)


df = read_rds(here::here("output","measures",filelist[6]))
# infection counts, population size, covid period
df = df%>% group_by(date, covid)%>% 
  summarise(counts=sum(infection_counts), 
            population=sum(population))
# month for seasonality
df$month= format(df$date,"%m")
# time elapsed(measurement time point) for linear effect of time to capture long-term behaviour trends
df$times <- as.numeric(as.factor(df$date))

#temp[[i]]=df

df6=df
rm(df)

```

```{r message=FALSE}
#df1=temp[[1]]#uti
#df2=temp[[2]]#urti
#df3=temp[[3]]#lrti
#df4=temp[[4]]#sinusitis
#df5=temp[[5]]#otitis externa
#df6=temp[[6]]#otitis media
#rm(temp)
```



# model2: Negative binomial model 

## UTI
```{r}
summary(m1.1 <- glm.nb(counts~ offset(log(population))+ covid + month + times + times*covid  , data = df1))
```

## URTI
```{r}
summary(m2.1 <- glm.nb(counts~ offset(log(population))+ covid + month + times + times*covid  , data = df2))
```

## LRTI
```{r}
summary(m3.1 <- glm.nb(counts~ offset(log(population))+ covid + month + times + times*covid  , data = df3))
```

## sinusitis
```{r}
summary(m4.1 <- glm.nb(counts~ offset(log(population))+ covid + month + times + times*covid  , data = df4))
```

## otitis externa
```{r}
summary(m5.1 <-glm.nb(counts~ offset(log(population))+ covid + month + times + times*covid  , data = df5))
```

## otitis media
```{r }
summary(m6.1 <- glm.nb(counts~ offset(log(population))+ covid + month + times + times*covid  , data = df6))
```



# model3: adding residual (for adjust autocorrelation)

```{r}
res1 <- residuals(m1.1,type="deviance")
res2 <- residuals(m2.1,type="deviance")
res3 <- residuals(m3.1,type="deviance")
res4 <- residuals(m4.1,type="deviance")
res5 <- residuals(m5.1,type="deviance")
res6 <- residuals(m6.1,type="deviance")

```


## UTI
```{r}
summary(m1.2 <- glm.nb(counts~ offset(log(population))+ covid + month + times + times*covid + res1  , data = df1))
```

## URTI
#Error in prettyNum(.Internal(format(x, trim, digits, nsmall, width, 3L,: invalid 'nsmall' argument
#https://stackoverflow.com/questions/64002936/error-in-prettynum-internalformatx-trim-digits-nsmall-width-3l-invalid
```{r}
summary(m2.2 <- glm.nb(counts~ offset(log(population))+ covid + month + times + times*covid + res2 , data = df2, control = glm.control(maxit = 500)))
```

## LRTI
```{r}
summary(m3.2 <- glm.nb(counts~ offset(log(population))+ covid + month + times + times*covid + res3  , data = df3))
```

## sinusitis
```{r}
summary(m4.2 <- glm.nb(counts~ offset(log(population))+ covid + month + times + times*covid + res4  , data = df4))
```

## otitis externa
```{r}
summary(m5.2 <-glm.nb(counts~ offset(log(population))+ covid + month + times + times*covid + res5  , data = df5))
```

## otitis media
```{r }
summary(m6.2 <- glm.nb(counts~ offset(log(population))+ covid + month + times + times*covid + res6  , data = df6))
```


```{r message=FALSE, include=FALSE}
### confidence intervals for the coefficients
(est1.2 <- cbind(Estimate = coef(m1.2), confint(m1.2)))
(est2.2 <- cbind(Estimate = coef(m2.2), confint(m2.2)))
(est3.2 <- cbind(Estimate = coef(m3.2), confint(m3.2)))
(est4.2 <- cbind(Estimate = coef(m4.2), confint(m4.2)))
(est5.2 <- cbind(Estimate = coef(m5.2), confint(m5.2)))
(est6.2 <- cbind(Estimate = coef(m6.2), confint(m6.2)))

```


```{r message=FALSE}
### calculate IRR & 95%CI
est1.2=exp(est1.2)
est2.2=exp(est2.2)
est3.2=exp(est3.2)
est4.2=exp(est4.2)
est5.2=exp(est5.2)
est6.2=exp(est6.2)
```

### covid
```{r message=FALSE}
## combine results
# covid
DF3=bind_rows(est1.2[2,],est2.2[2,],est3.2[2,],est4.2[2,],est5.2[2,],est6.2[2,])
DF3$Infection=c("UTI","URTI","LRTI","Sinusitis","Otitis externa","Otitis media")
#reorder
DF3=DF3%>%arrange(Infection)

names(DF3)[1]="IRR"
names(DF3)[2]="ci_l"
names(DF3)[3]="ci_u"

DF3
```


```{r message=FALSE}
### Model2_result
#setting up the basic plot
p3 <- ggplot(data=DF3, aes(y=Infection, x=IRR, xmin=ci_l, xmax=ci_u))+ 

#this adds the effect sizes to the plot
geom_point()+ 

#adds the CIs
geom_errorbarh(height=.1)+

#adding a vertical line at the effect = 0 mark
geom_vline(xintercept=1, color="black", linetype="dashed", alpha=.5)+
  
#thematic stuff
theme_minimal()+
theme(text=element_text(family="Times",size=18, color="black"))+
theme(panel.spacing = unit(1, "lines"))+

labs(
      title = "Consultation Reduction",
    x="IRR (95% CI)"
  )
```


### interaction
```{r}
## combine results
# covid*times
DF3.1=bind_rows(est1.2[15,],est2.2[15,],est3.2[15,],est4.2[15,],est5.2[15,],est6.2[15,])
DF3.1$Infection=c("UTI","URTI","LRTI","Sinusitis","Otitis externa","Otitis media")
#reorder
DF3.1=DF3.1%>%arrange(Infection)

names(DF3.1)[1]="IRR"
names(DF3.1)[2]="ci_l"
names(DF3,1)[3]="ci_u"

DF3.1
```

```{r}
### Model2_result
#setting up the basic plot
p3.1 <- ggplot(data=DF3.1, aes(y=Infection, x=IRR, xmin=ci_l, xmax=ci_u))+ 

#this adds the effect sizes to the plot
geom_point()+ 

#adds the CIs
geom_errorbarh(height=.1)+

#adding a vertical line at the effect = 0 mark
geom_vline(xintercept=1, color="black", linetype="dashed", alpha=.5)+
  
#thematic stuff
theme_minimal()+
theme(text=element_text(family="Times",size=18, color="black"))+
theme(panel.spacing = unit(1, "lines"))+

labs(
      title = "Interaction(Covid*times)",
    x="IRR (95% CI)"
  )
```



## model_3:  results

### covid 
```{r}
p3
```

### interaction
```{r}
p3.1
```


## compare models: model2 vs. model3
##UTI
```{r}
anova(m1.1,m1.2)

```


## URTI
```{r}
anova(m2.1,m2.2)

```


## LRTI
```{r}
anova(m3.1,m3.2)

```


## sinusitis
```{r}
anova(m4.1,m4.2)

```


## otitis externa
```{r}
anova(m5.1,m5.2)

```


## otitis media
```{r}
anova(m6.1,m6.2)

```


# Model checking and autocorrelation


# Model checking and autocorrelation
## model 2
### UTI
```{r}
#b) 
# Check the residuals by plotting against time
rm(res1)
res1 <- residuals(m1.2,type="deviance")
plot(df1$date,res1,ylim=c(-5,10),pch=19,cex=0.7,col=grey(0.6),
     main="Residuals over time",ylab="Deviance residuals",xlab="Date")
abline(h=0,lty=2,lwd=2)

# Further check for autocorrelation by examining the autocorrelation and
#   partial autocorrelation functions
acf(res1,lag.max=32)
pacf(res1,lag.max=32)

```

### LRTI
```{r}
#b) 
# Check the residuals by plotting against time
rm(res2)
res2 <- residuals(m2.2,type="deviance")
plot(df2$date,res2,ylim=c(-5,10),pch=19,cex=0.7,col=grey(0.6),
     main="Residuals over time",ylab="Deviance residuals",xlab="Date")
abline(h=0,lty=2,lwd=2)

# Further check for autocorrelation by examining the autocorrelation and
#   partial autocorrelation functions
acf(res2,lag.max=32)
pacf(res2,lag.max=32)

```

### URTI
```{r}
#b) 
# Check the residuals by plotting against time

rm(res3)
res3 <- residuals(m3.2,type="deviance")
plot(df3$date,res3,ylim=c(-5,10),pch=19,cex=0.7,col=grey(0.6),
     main="Residuals over time",ylab="Deviance residuals",xlab="Date")
abline(h=0,lty=2,lwd=2)

# Further check for autocorrelation by examining the autocorrelation and
#   partial autocorrelation functions
acf(res3,lag.max=32)
pacf(res3,lag.max=32)

```

### Sinusitis
```{r}
#b) 
# Check the residuals by plotting against time
rm(res4)
res4 <- residuals(m4.2,type="deviance")
plot(df4$date,res4,ylim=c(-5,10),pch=19,cex=0.7,col=grey(0.6),
     main="Residuals over time",ylab="Deviance residuals",xlab="Date")
abline(h=0,lty=2,lwd=2)

# Further check for autocorrelation by examining the autocorrelation and
#   partial autocorrelation functions
acf(res4,lag.max=32)
pacf(res4,lag.max=32)

```


### Otitis externa
```{r}
#b) 
# Check the residuals by plotting against time
rm(res5)
res5 <- residuals(m5.2,type="deviance")
plot(df5$date,res5,ylim=c(-5,10),pch=19,cex=0.7,col=grey(0.6),
     main="Residuals over time",ylab="Deviance residuals",xlab="Date")
abline(h=0,lty=2,lwd=2)

# Further check for autocorrelation by examining the autocorrelation and
#   partial autocorrelation functions
acf(res5,lag.max=32)
pacf(res5,lag.max=32)

```

### Otitis media
```{r}
#b) 
# Check the residuals by plotting against time
rm(res6)
res6 <- residuals(m6.2,type="deviance")
plot(df6$date,res6,ylim=c(-5,10),pch=19,cex=0.7,col=grey(0.6),
     main="Residuals over time",ylab="Deviance residuals",xlab="Date")
abline(h=0,lty=2,lwd=2)

# Further check for autocorrelation by examining the autocorrelation and
#   partial autocorrelation functions
acf(res6,lag.max=32)
pacf(res6,lag.max=32)

```