---
title: "consultation rate - ITS : ZERO-TRUNCATED NEGATIVE BINOMIAL"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir = '/workspace')
```

## Interrupted time-series analysis

```{r message=FALSE}
library("ggplot2")
library("data.table")
library("dplyr")
library("tidyverse")
library("MASS")
library("VGAM")
#library("gtsummary")
```

```{r message=FALSE}
### Import data
filelist=c("consult_UTI.rds","consult_URTI.rds","consult_LRTI.rds","consult_sinusitis.rds","consult_ot_externa.rds","consult_otmedia.rds")
#df=read_rds(paste0("/Users/yayang/Documents/GitHub/amr-uom-brit/output/measures/",filelist[1]))
df = read_rds(here::here("output","measures",filelist[1]))
# infection counts, population size, covid period
df = df%>% group_by(date, covid)%>% 
  summarise(counts=sum(infection_counts), 
            population=sum(population))
# month for seasonality
df$month= format(df$date,"%m")
# time elapsed(measurement time point) for linear effect of time to capture long-term behaviour trends
df$times <- as.numeric(as.factor(df$date))

df1=df
rm(df)

#df=read_rds(paste0("/Users/yayang/Documents/GitHub/amr-uom-brit/output/measures/",filelist[2]))
df = read_rds(here::here("output","measures",filelist[2]))
# infection counts, population size, covid period
df = df%>% group_by(date, covid)%>% 
  summarise(counts=sum(infection_counts), 
            population=sum(population))
# month for seasonality
df$month= format(df$date,"%m")
# time elapsed(measurement time point) for linear effect of time to capture long-term behaviour trends
df$times <- as.numeric(as.factor(df$date))



df2=df
rm(df)
#df=read_rds(paste0("/Users/yayang/Documents/GitHub/amr-uom-brit/output/measures/",filelist[3]))
df = read_rds(here::here("output","measures",filelist[3]))
# infection counts, population size, covid period
df = df%>% group_by(date, covid)%>% 
  summarise(counts=sum(infection_counts), 
            population=sum(population))
# month for seasonality
df$month= format(df$date,"%m")
# time elapsed(measurement time point) for linear effect of time to capture long-term behaviour trends
df$times <- as.numeric(as.factor(df$date))



df3=df
rm(df)
#df=read_rds(paste0("/Users/yayang/Documents/GitHub/amr-uom-brit/output/measures/",filelist[4]))
df = read_rds(here::here("output","measures",filelist[4]))
# infection counts, population size, covid period
df = df%>% group_by(date, covid)%>% 
  summarise(counts=sum(infection_counts), 
            population=sum(population))
# month for seasonality
df$month= format(df$date,"%m")
# time elapsed(measurement time point) for linear effect of time to capture long-term behaviour trends
df$times <- as.numeric(as.factor(df$date))

df4=df
rm(df)
#df=read_rds(paste0("/Users/yayang/Documents/GitHub/amr-uom-brit/output/measures/",filelist[5]))
df = read_rds(here::here("output","measures",filelist[5]))
# infection counts, population size, covid period
df = df%>% group_by(date, covid)%>% 
  summarise(counts=sum(infection_counts), 
            population=sum(population))
# month for seasonality
df$month= format(df$date,"%m")
# time elapsed(measurement time point) for linear effect of time to capture long-term behaviour trends
df$times <- as.numeric(as.factor(df$date))

df5=df
rm(df)
#df=read_rds(paste0("/Users/yayang/Documents/GitHub/amr-uom-brit/output/measures/",filelist[6]))
df = read_rds(here::here("output","measures",filelist[6]))
# infection counts, population size, covid period
df = df%>% group_by(date, covid)%>% 
  summarise(counts=sum(infection_counts), 
            population=sum(population))
# month for seasonality
df$month= format(df$date,"%m")
# time elapsed(measurement time point) for linear effect of time to capture long-term behaviour trends
df$times <- as.numeric(as.factor(df$date))


df6=df
rm(df)

```

# model1: seasonality adjusted by month
##UTI
```{r}
summary(m1 <- vglm(counts~ offset(log(population))+ covid + month +times+ covid*times , family = posnegbinomial(), data = df1))
```

## URTI
```{r}
summary(m2 <- vglm(counts~ offset(log(population))+ covid + month +times+ covid*times , family = posnegbinomial(), data = df2))
```

## LRTI
```{r}
summary(m3 <- vglm(counts~ offset(log(population))+ covid + month +times+ covid*times , family = posnegbinomial(), data = df3))
```

## Sinusitis
```{r}
summary(m4 <- vglm(counts~ offset(log(population))+ covid + month +times+ covid*times , family = posnegbinomial(), data = df4))
```

## otitis externa
```{r}
summary(m5 <- vglm(counts~ offset(log(population))+ covid + month +times+ covid*times , family = posnegbinomial(), data = df5))

```

## otitis media
```{r}
summary(m6 <- vglm(counts~ offset(log(population))+ covid + month +times+ covid*times , family = posnegbinomial(), data = df6))
```


```{r message=FALSE, include=FALSE}
### confidence intervals for the coefficients
(est1 <- cbind(Estimate = coef(m1), confint(m1)))
(est2 <- cbind(Estimate = coef(m2), confint(m2)))
(est3 <- cbind(Estimate = coef(m3), confint(m3)))
(est4 <- cbind(Estimate = coef(m4), confint(m4)))
(est5 <- cbind(Estimate = coef(m5), confint(m5)))
(est6 <- cbind(Estimate = coef(m6), confint(m6)))

```


```{r message=FALSE}
### calculate IRR & 95%CI
est1=exp(est1)
est2=exp(est2)
est3=exp(est3)
est4=exp(est4)
est5=exp(est5)
est6=exp(est6)
```

###  covid 
```{r message=FALSE}
#### combined results
DF=bind_rows(est1[3,],est2[3,],est3[3,],est4[3,],est5[3,],est6[3,])

DF$Infection=c("UTI","URTI","LRTI","Sinusitis","Otitis externa","Otitis media")
#reorder
DF=DF%>%arrange(Infection)

names(DF)[1]="IRR"
names(DF)[2]="ci_l"
names(DF)[3]="ci_u"
DF
```


```{r message=FALSE}
### result_model1
#setting up the basic plot
p1 <- ggplot(data=DF, aes(y=Infection, x=IRR, xmin=ci_l, xmax=ci_u))+ 

#this adds the effect sizes to the plot
geom_point()+ 

#adds the CIs
geom_errorbarh(height=.1)+

#adding a vertical line at the effect = 0 mark
geom_vline(xintercept=1, color="black", linetype="dashed", alpha=.5)+
  
#thematic stuff
theme_minimal()+
theme(text=element_text(family="Times",size=18, color="black"))+
theme(panel.spacing = unit(1, "lines"))+

labs(
    title = "Consultation Reduction",
    x="IRR (95% CI)"
  )

```

### interaction (covid*times)
```{r}
## combine results
# covid*times
DF1=bind_rows(est1[16,],est2[16,],est3[16,],est4[16,],est5[16,],est6[16,])
DF1$Infection=c("UTI","URTI","LRTI","Sinusitis","Otitis externa","Otitis media")
#reorder
DF1=DF1%>%arrange(Infection)

names(DF1)[1]="IRR"
names(DF1)[2]="ci_l"
names(DF1)[3]="ci_u"

DF1
```

```{r}
### Model2_result
#setting up the basic plot
p1.1 <- ggplot(data=DF1, aes(y=Infection, x=IRR, xmin=ci_l, xmax=ci_u))+ 

#this adds the effect sizes to the plot
geom_point()+ 

#adds the CIs
geom_errorbarh(height=.1)+

#adding a vertical line at the effect = 0 mark
geom_vline(xintercept=1, color="black", linetype="dashed", alpha=.5)+
  
#thematic stuff
theme_minimal()+
theme(text=element_text(family="Times",size=18, color="black"))+
theme(panel.spacing = unit(1, "lines"))+

labs(
      title = "Interaction(Covid*times)",
    x="IRR (95% CI)"
  )
```



# model2: seasonality adjusted by 4 seasons

```{r message=FALSE}
# month: categorical variables
df1$month=as.character(df1$month)
df2$month=as.character(df2$month)
df3$month=as.character(df3$month)
df4$month=as.character(df4$month)
df5$month=as.character(df5$month)
df6$month=as.character(df6$month)

df1=df1%>%mutate(season= case_when(month=="12"|month=="01"|month=="02" ~ "winter",
                                   month=="03"|month=="04"|month=="05" ~"spring",
                                   month=="06"|month=="07"|month=="08" ~"summer",
                                   month=="09"|month=="10"|month=="11" ~"autumn"))
df1$month=df1$season
df2=df2%>%mutate(season= case_when(month=="12"|month=="01"|month=="02" ~ "winter",
                                   month=="03"|month=="04"|month=="05" ~"spring",
                                   month=="06"|month=="07"|month=="08" ~"summer",
                                   month=="09"|month=="10"|month=="11" ~"autumn"))
df2$month=df2$season
df3=df3%>%mutate(season= case_when(month=="12"|month=="01"|month=="02" ~ "winter",
                                   month=="03"|month=="04"|month=="05" ~"spring",
                                   month=="06"|month=="07"|month=="08" ~"summer",
                                   month=="09"|month=="10"|month=="11" ~"autumn"))
df3$month=df3$season
df4=df4%>%mutate(season= case_when(month=="12"|month=="01"|month=="02" ~ "winter",
                                   month=="03"|month=="04"|month=="05" ~"spring",
                                   month=="06"|month=="07"|month=="08" ~"summer",
                                   month=="09"|month=="10"|month=="11" ~"autumn"))
df4$month=df4$season
df5=df5%>%mutate(season= case_when(month=="12"|month=="01"|month=="02" ~ "winter",
                                   month=="03"|month=="04"|month=="05" ~"spring",
                                   month=="06"|month=="07"|month=="08" ~"summer",
                                   month=="09"|month=="10"|month=="11" ~"autumn"))
df5$month=df5$season
df6=df6%>%mutate(season= case_when(month=="12"|month=="01"|month=="02" ~ "winter",
                                   month=="03"|month=="04"|month=="05" ~"spring",
                                   month=="06"|month=="07"|month=="08" ~"summer",
                                   month=="09"|month=="10"|month=="11" ~"autumn"))
df6$month=df6$season
```

##UTI
```{r}
summary(m1.1 <- vglm(counts~ offset(log(population))+ covid + month +times+ covid*times , family = posnegbinomial(), data = df1))
```

## URTI
```{r}
summary(m2.1 <- vglm(counts~ offset(log(population))+ covid + month +times+ covid*times , family = posnegbinomial(), data = df2))
```

## LRTI
```{r}
summary(m3.1 <- vglm(counts~ offset(log(population))+ covid + month +times+ covid*times , family = posnegbinomial(), data = df3))
```

## Sinusitis
```{r}
summary(m4.1 <- vglm(counts~ offset(log(population))+ covid + month +times+ covid*times , family = posnegbinomial(), data = df4))
```

## otitis externa
```{r}
summary(m5.1 <- vglm(counts~ offset(log(population))+ covid + month +times+ covid*times , family = posnegbinomial(), data = df5))

```

## otitis media
```{r}
summary(m6.1 <- vglm(counts~ offset(log(population))+ covid + month +times+ covid*times , family = posnegbinomial(), data = df6))
```


```{r message=FALSE, include=FALSE}
### confidence intervals for the coefficients
(est1.1 <- cbind(Estimate = coef(m1.1), confint(m1.1)))
(est2.1 <- cbind(Estimate = coef(m2.1), confint(m2.1)))
(est3.1 <- cbind(Estimate = coef(m3.1), confint(m3.1)))
(est4.1 <- cbind(Estimate = coef(m4.1), confint(m4.1)))
(est5.1 <- cbind(Estimate = coef(m5.1), confint(m5.1)))
(est6.1 <- cbind(Estimate = coef(m6.1), confint(m6.1)))

```


```{r message=FALSE}
### calculate IRR & 95%CI
est1.1=exp(est1.1)
est2.1=exp(est2.1)
est3.1=exp(est3.1)
est4.1=exp(est4.1)
est5.1=exp(est5.1)
est6.1=exp(est6.1)
```

### covid
```{r message=FALSE}
## combine results
# covid
DF2=bind_rows(est1.1[3,],est2.1[3,],est3.1[3,],est4.1[3,],est5.1[3,],est6.1[3,])
DF2$Infection=c("UTI","URTI","LRTI","Sinusitis","Otitis externa","Otitis media")
#reorder
DF2=DF2%>%arrange(Infection)

names(DF2)[1]="IRR"
names(DF2)[2]="ci_l"
names(DF2)[3]="ci_u"

DF2
```


```{r message=FALSE}
### Model2_result
#setting up the basic plot
p2 <- ggplot(data=DF2, aes(y=Infection, x=IRR, xmin=ci_l, xmax=ci_u))+ 

#this adds the effect sizes to the plot
geom_point()+ 

#adds the CIs
geom_errorbarh(height=.1)+

#adding a vertical line at the effect = 0 mark
geom_vline(xintercept=1, color="black", linetype="dashed", alpha=.5)+
  
#thematic stuff
theme_minimal()+
theme(text=element_text(family="Times",size=18, color="black"))+
theme(panel.spacing = unit(1, "lines"))+

labs(
      title = "Consultation Reduction",
    x="IRR (95% CI)"
  )
```


### interaction 
```{r}
## combine results
# covid*times
DF2.1=bind_rows(est1.1[8,],est2.1[8,],est3.1[8,],est4.1[8,],est5.1[8,],est6.1[8,])
DF2.1$Infection=c("UTI","URTI","LRTI","Sinusitis","Otitis externa","Otitis media")
#reorder
DF2.1=DF2.1%>%arrange(Infection)

names(DF2.1)[1]="IRR"
names(DF2.1)[2]="ci_l"
names(DF2.1)[3]="ci_u"

DF2.1
```

```{r}
### Model2_result
#setting up the basic plot
p2.1 <- ggplot(data=DF2.1, aes(y=Infection, x=IRR, xmin=ci_l, xmax=ci_u))+ 

#this adds the effect sizes to the plot
geom_point()+ 

#adds the CIs
geom_errorbarh(height=.1)+

#adding a vertical line at the effect = 0 mark
geom_vline(xintercept=1, color="black", linetype="dashed", alpha=.5)+
  
#thematic stuff
theme_minimal()+
theme(text=element_text(family="Times",size=18, color="black"))+
theme(panel.spacing = unit(1, "lines"))+

labs(
      title = "Interaction(Covid*times)",
    x="IRR (95% CI)"
  )
```


# comparing results
## month model

### covid
```{r}
p1
```

### slope change (interaction)
```{r}
p1.1
```

## seasons model

### covid
```{r}
p2
```

### slope change (interaction)
```{r}
p2.1
```


## comparing models

##UTI
### model 1 vs. model2 (with or without interaction)
```{r}
anova(m1,m1.1)

```


## URTI
### model 1 vs. model2 (with or without interaction)
```{r}
anova(m2,m2.1)

```


## LRTI
### model 1 vs. model2 (with or without interaction)
```{r}
anova(m3,m3.1)

```


## sinusitis
### model 1 vs. model2 (with or without interaction)
```{r}
anova(m4,m4.1)

```


## otitis externa
### model 1 vs. model2 (with or without interaction)
```{r}
anova(m5,m5.1)

```


## otitis media
### model 1 vs. model2 (with or without interaction)
```{r}
anova(m6,m6.1)

```




# Model checking and autocorrelation
## month model
### UTI
```{r}
#b) 
# Check the residuals by plotting against time
res1 <- residuals(m1,type="deviance")
plot(df1$date,res1,ylim=c(-5,10),pch=19,cex=0.7,col=grey(0.6),
     main="Residuals over time",ylab="Deviance residuals",xlab="Date")
abline(h=0,lty=2,lwd=2)

# Further check for autocorrelation by examining the autocorrelation and
#   partial autocorrelation functions

acf(res1,lag.max=32)
pacf(res1,lag.max=32)
rm(res1)
```

### LRTI
```{r}
#b) 
# Check the residuals by plotting against time
res2 <- residuals(m2,type="deviance")
plot(df2$date,res2,ylim=c(-5,10),pch=19,cex=0.7,col=grey(0.6),
     main="Residuals over time",ylab="Deviance residuals",xlab="Date")
abline(h=0,lty=2,lwd=2)

# Further check for autocorrelation by examining the autocorrelation and
#   partial autocorrelation functions

acf(res2,lag.max=32)
pacf(res2,lag.max=32)
rm(res2)
```

### URTI
```{r}
#b) 
# Check the residuals by plotting against time
res3 <- residuals(m3,type="deviance")
plot(df3$date,res3,ylim=c(-5,10),pch=19,cex=0.7,col=grey(0.6),
     main="Residuals over time",ylab="Deviance residuals",xlab="Date")
abline(h=0,lty=2,lwd=2)

# Further check for autocorrelation by examining the autocorrelation and
#   partial autocorrelation functions

acf(res3,lag.max=32)
pacf(res3,lag.max=32)
rm(res3)
```

### Sinusitis
```{r}
#b) 
# Check the residuals by plotting against time
res4 <- residuals(m4,type="deviance")
plot(df4$date,res4,ylim=c(-5,10),pch=19,cex=0.7,col=grey(0.6),
     main="Residuals over time",ylab="Deviance residuals",xlab="Date")
abline(h=0,lty=2,lwd=2)

# Further check for autocorrelation by examining the autocorrelation and
#   partial autocorrelation functions


acf(res4,lag.max=32)
pacf(res4,lag.max=32)
rm(res4)
```


### Otitis externa
```{r}
#b) 
# Check the residuals by plotting against time
res5 <- residuals(m5,type="deviance")
plot(df5$date,res5,ylim=c(-5,10),pch=19,cex=0.7,col=grey(0.6),
     main="Residuals over time",ylab="Deviance residuals",xlab="Date")
abline(h=0,lty=2,lwd=2)

# Further check for autocorrelation by examining the autocorrelation and
#   partial autocorrelation functions


acf(res5,lag.max=32)
pacf(res5,lag.max=32)
rm(res5)
```

### Otitis media
```{r}
#b) 
# Check the residuals by plotting against time
res6 <- residuals(m6,type="deviance")
plot(df6$date,res6,ylim=c(-5,10),pch=19,cex=0.7,col=grey(0.6),
     main="Residuals over time",ylab="Deviance residuals",xlab="Date")
abline(h=0,lty=2,lwd=2)

# Further check for autocorrelation by examining the autocorrelation and
#   partial autocorrelation functions

acf(res6,lag.max=32)
pacf(res6,lag.max=32)
rm(res6)
```

## seasons model
### UTI
```{r}
#b) 
# Check the residuals by plotting against time
res1 <- residuals(m1.1,type="deviance")
plot(df1$date,res1,ylim=c(-5,10),pch=19,cex=0.7,col=grey(0.6),
     main="Residuals over time",ylab="Deviance residuals",xlab="Date")
abline(h=0,lty=2,lwd=2)

# Further check for autocorrelation by examining the autocorrelation and
#   partial autocorrelation functions


acf(res1,lag.max=32)
pacf(res1,lag.max=32)
rm(res1)
```

### LRTI
```{r}
#b) 
# Check the residuals by plotting against time
res2 <- residuals(m2.1,type="deviance")
plot(df2$date,res2,ylim=c(-5,10),pch=19,cex=0.7,col=grey(0.6),
     main="Residuals over time",ylab="Deviance residuals",xlab="Date")
abline(h=0,lty=2,lwd=2)

# Further check for autocorrelation by examining the autocorrelation and
#   partial autocorrelation functions


acf(res2,lag.max=32)
pacf(res2,lag.max=32)
rm(res2)
```

### URTI
```{r}
#b) 
# Check the residuals by plotting against time
res3 <- residuals(m3.1,type="deviance")
plot(df3$date,res3,ylim=c(-5,10),pch=19,cex=0.7,col=grey(0.6),
     main="Residuals over time",ylab="Deviance residuals",xlab="Date")
abline(h=0,lty=2,lwd=2)

# Further check for autocorrelation by examining the autocorrelation and
#   partial autocorrelation functions


acf(res3,lag.max=32)
pacf(res3,lag.max=32)
rm(res3)
```

### Sinusitis
```{r}
#b) 
# Check the residuals by plotting against time
res4 <- residuals(m4.1,type="deviance")
plot(df4$date,res4,ylim=c(-5,10),pch=19,cex=0.7,col=grey(0.6),
     main="Residuals over time",ylab="Deviance residuals",xlab="Date")
abline(h=0,lty=2,lwd=2)

# Further check for autocorrelation by examining the autocorrelation and
#   partial autocorrelation functions

acf(res4,lag.max=32)
pacf(res4,lag.max=32)
rm(res4)
```


### Otitis externa
```{r}
#b) 
# Check the residuals by plotting against time
res5 <- residuals(m5.1,type="deviance")
plot(df5$date,res5,ylim=c(-5,10),pch=19,cex=0.7,col=grey(0.6),
     main="Residuals over time",ylab="Deviance residuals",xlab="Date")
abline(h=0,lty=2,lwd=2)

# Further check for autocorrelation by examining the autocorrelation and
#   partial autocorrelation functions

acf(res5,lag.max=32)
pacf(res5,lag.max=32)
rm(res5)
```

### Otitis media
```{r}
#b) 
# Check the residuals by plotting against time
res6 <- residuals(m6.1,type="deviance")
plot(df6$date,res6,ylim=c(-5,10),pch=19,cex=0.7,col=grey(0.6),
     main="Residuals over time",ylab="Deviance residuals",xlab="Date")
abline(h=0,lty=2,lwd=2)

# Further check for autocorrelation by examining the autocorrelation and
#   partial autocorrelation functions

acf(res6,lag.max=32)
pacf(res6,lag.max=32)
rm(res6)
```


