---
title: "antibiotics exposure btw case/control"
---

```{r setup, include=FALSE}
library('tidyverse')
library("ggplot2")
library('dplyr')
library('lubridate')
library('stringr')
library("data.table")
library("ggpubr")
library("finalfit")
```


# read table
```{r}
data=read_rds(here::here("output","all_ranger.rds"))
data$decile=as.factor(data$decile)
data$case=as.factor(data$case)
```

# categorised ab exposure variables
```{r eval=FALSE, include=FALSE}
col=c("case","subclass",
  "total_ab","ab_types","prescribe_times",
         "exposure_period","recent_ab_days", 
         "broad_prop","broad_ab_prescriptions",
         "interval_mean","interval_med" ,"interval_sd","interval_CV",
         "length_mean","length_med", "length_sd","length_CV")

data=data %>% mutate_at(col,as.numeric)
names(data)

for (k in 3:17) {

cut_value=quantile(data[,col[k]],c(0.25,0.5,0.75))
print(cut_value)
  
data[,paste0(col[k],"_group")]=ifelse(
  data[,col[k]] <= cut_value[1],1,NA)  

data[,paste0(col[k],"_group")]=ifelse(
  data[,col[k]] > cut_value[1] & data[,col[k]]<= cut_value[2],2, 
  data[,paste0(col[k],"_group")])  

data[,paste0(col[k],"_group")]=ifelse(
  data[,col[k]] > cut_value[2] & data[,col[k]]<= cut_value[3],3, 
  data[,paste0(col[k],"_group")])  

data[,paste0(col[k],"_group")]=ifelse(
  data[,col[k]] > cut_value[3],4,data[,paste0(col[k],"_group")])  

data[,paste0(col[k],"_group")]=ifelse(
 is.na( data[,col[k]]) ,0 ,data[,paste0(col[k],"_group")])  



}

data$total_ab_group=relevel(as.factor(data$total_ab_group),ref= "1")
data$ab_types_group=relevel(as.factor(data$ab_types_group),ref= "1")
data$exposure_period_group=relevel(as.factor(data$exposure_period_group),ref= "1")
data$recent_ab_days_group=relevel(as.factor(data$recent_ab_days_group),ref= "1")
data$broad_prop_group=relevel(as.factor(data$broad_prop_group),ref= "1")
data$broad_ab_prescriptions_group=relevel(as.factor(data$broad_ab_prescriptions_group),ref= "1")
data$interval_mean_group=relevel(as.factor(data$interval_mean_group),ref= "1")
data$interval_med_group=relevel(as.factor(data$interval_med_group),ref= "1")
data$interval_CV_group=relevel(as.factor(data$interval_CV_group),ref= "1")
data$interval_sd_group=relevel(as.factor(data$interval_sd_group),ref= "1")
data$length_med_group=relevel(as.factor(data$length_med_group),ref= "1")
data$length_mean_group=relevel(as.factor(data$length_mean_group),ref= "1")
data$length_CV_group=relevel(as.factor(data$length_CV_group),ref= "1")
data$length_sd_group=relevel(as.factor(data$length_sd_group),ref= "1")
```

# variability
## prediction
```{r}
data$case=as.factor(data$case)
data$decile=as.factor(data$decile)

## quantiles
quantiles1 <- data %>% group_by(case,decile)%>%
summarise(med = quantile(prob, na.rm=TRUE)[3],
         lowquart= quantile(prob, na.rm=TRUE)[2],
         highquart= quantile(prob, na.rm=TRUE)[4],
         ninefive= quantile(prob, na.rm=TRUE, c(0.95)),
         five=quantile(prob, na.rm=TRUE, c(0.05)),
         variable="prob")

plot<- ggplot(quantiles1, aes(x=decile,group=case))+
    geom_ribbon(aes(ymin = five, ymax = ninefive ), fill = "grey60",alpha=0.3) +  
  geom_ribbon(aes(ymin =lowquart, ymax =highquart ), fill = "grey70",alpha=0.6) +  
    geom_line(aes(y=med))+
    geom_point(aes(y=med))+
  #  geom_line(aes(y=lowquart), color="darkred")+
  #  geom_point(aes(y=lowquart), color="darkred")+
  #  geom_line(aes(y=highquart), color="darkred")+
 #   geom_point(aes(y=highquart), color="darkred")+

  #  geom_line(aes(y=ninefive), color="black", linetype="dotted")+
  #  geom_point(aes(y=ninefive), color="black")+
  #  geom_line(aes(y=five), color="black", linetype="dotted")+
  #  geom_point(aes(y=five), color="black")+
    labs(
      title = "",
      x = "",
      y = "")+
  facet_grid(case~.)
plot
```


## total antibiotics
```{r}
## quantiles
quantiles2 <- data %>% group_by(case,decile)%>%
summarise(med = quantile(total_ab, na.rm=TRUE)[3],
         lowquart= quantile(total_ab, na.rm=TRUE)[2],
         highquart= quantile(total_ab, na.rm=TRUE)[4],
         ninefive= quantile(total_ab, na.rm=TRUE, c(0.95)),
         five=quantile(total_ab, na.rm=TRUE, c(0.05)),
         variable="total_ab")

plot<- ggplot(quantiles2, aes(x=decile,group=case))+
    geom_ribbon(aes(ymin = five, ymax = ninefive ), fill = "grey60",alpha=0.3) +  
  geom_ribbon(aes(ymin =lowquart, ymax =highquart ), fill = "grey70",alpha=0.6) +  
    geom_line(aes(y=med))+
    geom_point(aes(y=med))+
    labs(
      title = "",
      x = "",
      y = "")+
  facet_grid(case~.)
plot
```

## ab types
```{r}
## quantiles
quantiles3 <- data %>% group_by(case,decile)%>%
  summarise(med = quantile(ab_types, na.rm=TRUE)[3],
         lowquart= quantile(ab_types, na.rm=TRUE)[2],
         highquart= quantile(ab_types, na.rm=TRUE)[4],
         ninefive= quantile(ab_types, na.rm=TRUE, c(0.95)),
         five=quantile(ab_types, na.rm=TRUE, c(0.05)),
         variable="ab_types")

plot<- ggplot(quantiles3, aes(x=decile,group=case))+
    geom_ribbon(aes(ymin = five, ymax = ninefive ), fill = "grey60",alpha=0.3) +  
  geom_ribbon(aes(ymin =lowquart, ymax =highquart ), fill = "grey70",alpha=0.6) +  
    geom_line(aes(y=med))+
    geom_point(aes(y=med))+
    labs(
      title = "",
      x = "",
      y = "")+
  facet_grid(case~.)
plot
```

## exposure_period
```{r}
## quantiles
quantiles4 <- data %>% group_by(case,decile)%>%
  summarise(med = quantile(exposure_period, na.rm=TRUE)[3],
         lowquart= quantile(exposure_period, na.rm=TRUE)[2],
         highquart= quantile(exposure_period, na.rm=TRUE)[4],
         ninefive= quantile(exposure_period, na.rm=TRUE, c(0.95)),
         five=quantile(exposure_period, na.rm=TRUE, c(0.05)),
         variable="expo_period")

plot<- ggplot(quantiles4, aes(x=decile,group=case))+
    geom_ribbon(aes(ymin = five, ymax = ninefive ), fill = "grey60",alpha=0.3) +  
  geom_ribbon(aes(ymin =lowquart, ymax =highquart ), fill = "grey70",alpha=0.6) +  
    geom_line(aes(y=med))+
    geom_point(aes(y=med))+
    labs(
      title = "",
      x = "",
      y = "")+
  facet_grid(case~.)
plot
```

## recent_ab_days
```{r}
## quantiles
quantiles5 <- data %>% group_by(case,decile)%>%
  summarise(med = quantile(recent_ab_days, na.rm=TRUE)[3],
         lowquart= quantile(recent_ab_days, na.rm=TRUE)[2],
         highquart= quantile(recent_ab_days, na.rm=TRUE)[4],
         ninefive= quantile(recent_ab_days, na.rm=TRUE, c(0.95)),
         five=quantile(recent_ab_days, na.rm=TRUE, c(0.05)),
         variable="recent_ab")

plot<- ggplot(quantiles5, aes(x=decile,group=case))+
    geom_ribbon(aes(ymin = five, ymax = ninefive ), fill = "grey60",alpha=0.3) +  
  geom_ribbon(aes(ymin =lowquart, ymax =highquart ), fill = "grey70",alpha=0.6) +  
    geom_line(aes(y=med))+
    geom_point(aes(y=med))+
    labs(
      title = "",
      x = "",
      y = "")+
  facet_grid(case~.)
plot
```

## broad_ab_prescriptions
```{r}
## quantiles
quantiles6 <- data %>% group_by(case,decile)%>%
  summarise(med = quantile(broad_ab_prescriptions, na.rm=TRUE)[3],
         lowquart= quantile(broad_ab_prescriptions, na.rm=TRUE)[2],
         highquart= quantile(broad_ab_prescriptions, na.rm=TRUE)[4],
         ninefive= quantile(broad_ab_prescriptions, na.rm=TRUE, c(0.95)),
         five=quantile(broad_ab_prescriptions, na.rm=TRUE, c(0.05)),
         variable="broad_ab")

plot<- ggplot(quantiles6, aes(x=decile,group=case))+
    geom_ribbon(aes(ymin = five, ymax = ninefive ), fill = "grey60",alpha=0.3) +  
  geom_ribbon(aes(ymin =lowquart, ymax =highquart ), fill = "grey70",alpha=0.6) +  
    geom_line(aes(y=med))+
    geom_point(aes(y=med))+
    labs(
      title = "",
      x = "",
      y = "")+
  facet_grid(case~.)
plot
```


## interval_mean
```{r}
## quantiles
quantiles7 <- data %>% group_by(case,decile)%>%
  summarise(med = quantile(interval_mean, na.rm=TRUE)[3],
         lowquart= quantile(interval_mean, na.rm=TRUE)[2],
         highquart= quantile(interval_mean, na.rm=TRUE)[4],
         ninefive= quantile(interval_mean, na.rm=TRUE, c(0.95)),
         five=quantile(interval_mean, na.rm=TRUE, c(0.05)),
         variable="interval_mean")

plot<- ggplot(quantiles7, aes(x=decile,group=case))+
    geom_ribbon(aes(ymin = five, ymax = ninefive ), fill = "grey60",alpha=0.3) +  
  geom_ribbon(aes(ymin =lowquart, ymax =highquart ), fill = "grey70",alpha=0.6) +  
    geom_line(aes(y=med))+
    geom_point(aes(y=med))+
    labs(
      title = "",
      x = "",
      y = "")+
  facet_grid(case~.)
plot
```

## interval_sd
```{r}
## quantiles
quantiles8 <- data %>% group_by(case,decile)%>%
  summarise(med = quantile(interval_sd, na.rm=TRUE)[3],
         lowquart= quantile(interval_sd, na.rm=TRUE)[2],
         highquart= quantile(interval_sd, na.rm=TRUE)[4],
         ninefive= quantile(interval_sd, na.rm=TRUE, c(0.95)),
         five=quantile(interval_sd, na.rm=TRUE, c(0.05)),
         variable="interval_sd")

plot<- ggplot(quantiles8, aes(x=decile,group=case))+
    geom_ribbon(aes(ymin = five, ymax = ninefive ), fill = "grey60",alpha=0.3) +  
  geom_ribbon(aes(ymin =lowquart, ymax =highquart ), fill = "grey70",alpha=0.6) +  
    geom_line(aes(y=med))+
    geom_point(aes(y=med))+
    labs(
      title = "",
      x = "",
      y = "")+
  facet_grid(case~.)
plot
```

# output data
```{r}
DF=rbind(quantiles1,quantiles2,quantiles3,quantiles4,quantiles5,quantiles6,quantiles7,quantiles8)
write.csv(DF, here::here("output","quantile_outcome.csv"))
```

## total_ab
```{r}

plot<- ggplot(data, aes(x=total_ab,y=prob,group=decile))+
    geom_point()+
    labs(
      title = "",
      x = "",
      y = "")+
  facet_grid(case~.)
plot
```

## ab_types
```{r}

plot<- ggplot(data, aes(x=ab_types,y=prob,group=decile))+
    geom_point()+
    labs(
      title = "",
      x = "",
      y = "")+
  facet_grid(case~.)
plot
```


## exposure_period
```{r}

plot<- ggplot(data, aes(x=exposure_period,y=prob,group=decile))+
    geom_point()+
    labs(
      title = "",
      x = "",
      y = "")+
  facet_grid(case~.)
plot
```

## recent_ab_days
```{r}

plot<- ggplot(data, aes(x=recent_ab_days,y=prob,group=decile))+
    geom_point()+
    labs(
      title = "",
      x = "",
      y = "")+
  facet_grid(case~.)
plot
```

## broad_ab_prescriptions
```{r}

plot<- ggplot(data, aes(x=broad_ab_prescriptions,y=prob,group=decile))+
    geom_point()+
    labs(
      title = "",
      x = "",
      y = "")+
  facet_grid(case~.)
plot
```

## interval_mean
```{r}

plot<- ggplot(data, aes(x=interval_mean,y=prob,group=decile))+
    geom_point()+
    labs(
      title = "",
      x = "",
      y = "")+
  facet_grid(case~.)
plot
```

## interval_sd
```{r}

plot<- ggplot(data, aes(x=interval_sd,y=prob,group=decile))+
    geom_point()+
    labs(
      title = "",
      x = "",
      y = "")+
  facet_grid(case~.)
plot
```

## total_ab
```{r}

plot<- ggplot(data, aes(x=total_ab,y=prob,group=decile))+
    geom_point()+
    labs(
      title = "",
      x = "",
      y = "")
plot
```

## ab_types
```{r}

plot<- ggplot(data, aes(x=ab_types,y=prob,group=decile))+
    geom_point()+
    labs(
      title = "",
      x = "",
      y = "")
plot
```


## exposure_period
```{r}

plot<- ggplot(data, aes(x=exposure_period,y=prob,group=decile))+
    geom_point()+
    labs(
      title = "",
      x = "",
      y = "")
plot
```

## recent_ab_days
```{r}

plot<- ggplot(data, aes(x=recent_ab_days,y=prob,group=decile))+
    geom_point()+
    labs(
      title = "",
      x = "",
      y = "")
plot
```

## broad_ab_prescriptions
```{r}

plot<- ggplot(data, aes(x=broad_ab_prescriptions,y=prob,group=decile))+
    geom_point()+
    labs(
      title = "",
      x = "",
      y = "")
plot
```

## interval_mean
```{r}

plot<- ggplot(data, aes(x=interval_mean,y=prob,group=decile))+
    geom_point()+
    labs(
      title = "",
      x = "",
      y = "")
plot
```

## interval_sd
```{r}

plot<- ggplot(data, aes(x=interval_sd,y=prob,group=decile))+
    geom_point()+
    labs(
      title = "",
      x = "",
      y = "")
plot
```





## total antibiotics
```{r}
## quantiles
quantiles2 <- data %>% group_by(decile)%>%
  summarise(med = quantile(total_ab, na.rm=TRUE)[3],
         lowquart= quantile(total_ab, na.rm=TRUE)[2],
         highquart= quantile(total_ab, na.rm=TRUE)[4],
         ninefive= quantile(total_ab, na.rm=TRUE, c(0.95)),
         five=quantile(total_ab, na.rm=TRUE, c(0.05)),
         variable="total_ab")

plot<- ggplot(quantiles2, aes(x=decile))+
#    geom_ribbon(aes(ymin = five, ymax = ninefive ), fill = "grey60",alpha=0.2) +  
#  geom_ribbon(aes(ymin =lowquart, ymax =highquart ), fill = "grey70",alpha=0.5) +  
    geom_line(aes(y=med))+
    geom_point(aes(y=med))+
      geom_line(aes(y=lowquart),color="blue", linetype="dotted")+
      geom_line(aes(y=highquart),color="blue", linetype="dotted")+
        geom_line(aes(y=ninefive),color="red", linetype="dotted")+
      geom_line(aes(y=five),color="red", linetype="dotted")+
  theme_bw()+
    labs(
      title = "",
      x = "",
      y = "")
plot
```

## ab types
```{r}
## quantiles
quantiles3 <- data %>% group_by(decile)%>%
   summarise(med = quantile(ab_types, na.rm=TRUE)[3],
         lowquart= quantile(ab_types, na.rm=TRUE)[2],
         highquart= quantile(ab_types, na.rm=TRUE)[4],
         ninefive= quantile(ab_types, na.rm=TRUE, c(0.95)),
         five=quantile(ab_types, na.rm=TRUE, c(0.05)),
         variable="ab_types")

plot<- ggplot(quantiles3, aes(x=decile))+
#    geom_ribbon(aes(ymin = five, ymax = ninefive ), fill = "grey60",alpha=0.2) +  
#  geom_ribbon(aes(ymin =lowquart, ymax =highquart ), fill = "grey70",alpha=0.5) +  
    geom_line(aes(y=med))+
    geom_point(aes(y=med))+
      geom_line(aes(y=lowquart),color="blue", linetype="dotted")+
      geom_line(aes(y=highquart),color="blue", linetype="dotted")+
        geom_line(aes(y=ninefive),color="red", linetype="dotted")+
      geom_line(aes(y=five),color="red", linetype="dotted")+
  theme_bw()+
    labs(
      title = "",
      x = "",
      y = "")
plot
```

## exposure_period
```{r}
## quantiles
quantiles4 <- data %>% group_by(decile)%>%
   summarise(med = quantile(exposure_period, na.rm=TRUE)[3],
         lowquart= quantile(exposure_period, na.rm=TRUE)[2],
         highquart= quantile(exposure_period, na.rm=TRUE)[4],
         ninefive= quantile(exposure_period, na.rm=TRUE, c(0.95)),
         five=quantile(exposure_period, na.rm=TRUE, c(0.05)),
         variable="expo_period")
quantiles4=quantiles4%>%ungroup(decile)
plot<- ggplot(quantiles4, aes(x=decile))+
   geom_ribbon(aes(ymin = five, ymax = ninefive ), fill = "grey60",alpha=0.2) +  
  geom_ribbon(aes(ymin =lowquart, ymax =highquart ), fill = "grey70",alpha=0.5) +  
    geom_line(aes(y=med))+
    geom_point(aes(y=med))+
 #     geom_line(aes(y=highquart),color="blue", linetype="dotted")+
#      geom_line(aes(y=lowquart),color="blue", linetype="dotted")+
    #  geom_line(aes(y=five),color="red", linetype="dotted")+
  ##      geom_line(aes(y=ninefive),color="red", linetype="dotted")+
  theme_bw()+
    labs(
      title = "",
      x = "",
      y = "")
plot
```

## recent_ab_days
```{r}
## quantiles
quantiles5 <- data %>% group_by(decile)%>%
  summarise(med = quantile(recent_ab_days, na.rm=TRUE)[3],
         lowquart= quantile(recent_ab_days, na.rm=TRUE)[2],
         highquart= quantile(recent_ab_days, na.rm=TRUE)[4],
         ninefive= quantile(recent_ab_days, na.rm=TRUE, c(0.95)),
         five=quantile(recent_ab_days, na.rm=TRUE, c(0.05)),
         variable="recent_ab")

plot<- ggplot(quantiles5, aes(x=decile))+
#    geom_ribbon(aes(ymin = five, ymax = ninefive ), fill = "grey60",alpha=0.2) +  
#  geom_ribbon(aes(ymin =lowquart, ymax =highquart ), fill = "grey70",alpha=0.5) +  
    geom_line(aes(y=med))+
    geom_point(aes(y=med))+
      geom_line(aes(y=lowquart),color="blue", linetype="dotted")+
      geom_line(aes(y=highquart),color="blue", linetype="dotted")+
        geom_line(aes(y=ninefive),color="red", linetype="dotted")+
      geom_line(aes(y=five),color="red", linetype="dotted")+
  theme_bw()+
    labs(
      title = "",
      x = "",
      y = "")
plot
```

## broad_ab_prescriptions
```{r}
## quantiles
quantiles6 <- data %>% group_by(decile)%>%
  summarise(med = quantile(broad_ab_prescriptions, na.rm=TRUE)[3],
         lowquart= quantile(broad_ab_prescriptions, na.rm=TRUE)[2],
         highquart= quantile(broad_ab_prescriptions, na.rm=TRUE)[4],
         ninefive= quantile(broad_ab_prescriptions, na.rm=TRUE, c(0.95)),
         five=quantile(broad_ab_prescriptions, na.rm=TRUE, c(0.05)),
         variable="broad_ab")

plot<- ggplot(quantiles6, aes(x=decile))+
#    geom_ribbon(aes(ymin = five, ymax = ninefive ), fill = "grey60",alpha=0.2) +  
#  geom_ribbon(aes(ymin =lowquart, ymax =highquart ), fill = "grey70",alpha=0.5) +  
    geom_line(aes(y=med))+
    geom_point(aes(y=med))+
      geom_line(aes(y=lowquart),color="blue", linetype="dotted")+
      geom_line(aes(y=highquart),color="blue", linetype="dotted")+
        geom_line(aes(y=ninefive),color="red", linetype="dotted")+
      geom_line(aes(y=five),color="red", linetype="dotted")+
  theme_bw()+
    labs(
      title = "",
      x = "",
      y = "")
plot
```


## interval_mean
```{r}
## quantiles
quantiles7 <- data %>% group_by(decile)%>%
  summarise(med = quantile(interval_mean, na.rm=TRUE)[3],
         lowquart= quantile(interval_mean, na.rm=TRUE)[2],
         highquart= quantile(interval_mean, na.rm=TRUE)[4],
         ninefive= quantile(interval_mean, na.rm=TRUE, c(0.95)),
         five=quantile(interval_mean, na.rm=TRUE, c(0.05)),
         variable="interval_mean")
quantiles7=quantiles7%>%ungroup(decile)
plot<- ggplot(quantiles7, aes(x=decile))+
    geom_ribbon(aes(ymin = five, ymax = ninefive ), fill = "grey60",alpha=0.2) +  
  geom_ribbon(aes(ymin =lowquart, ymax =highquart ), fill = "grey70",alpha=0.5) +  
    geom_line(aes(y=med))+
    geom_point(aes(y=med))+
  #    geom_line(aes(y=lowquart),color="blue", linetype="dotted")+
  #    geom_line(aes(y=highquart),color="blue", linetype="dotted")+
  #      geom_line(aes(y=ninefive),color="red", linetype="dotted")+
  #    geom_line(aes(y=five),color="red", linetype="dotted")+
  theme_bw()+
    labs(
      title = "",
      x = "",
      y = "")
plot
```

## interval_sd
```{r}
## quantiles
quantiles8 <- data %>% group_by(decile)%>%
 summarise(med = quantile(interval_sd, na.rm=TRUE)[3],
         lowquart= quantile(interval_sd, na.rm=TRUE)[2],
         highquart= quantile(interval_sd, na.rm=TRUE)[4],
         ninefive= quantile(interval_sd, na.rm=TRUE, c(0.95)),
         five=quantile(interval_sd, na.rm=TRUE, c(0.05)),
         variable="interval_sd")
quantiles8=quantiles8%>%ungroup(decile)

plot<- ggplot(quantiles8, aes(x=decile))+
    geom_ribbon(aes(ymin = five, ymax = ninefive ), fill = "grey60",alpha=0.2) +  
  geom_ribbon(aes(ymin =lowquart, ymax =highquart ), fill = "grey70",alpha=0.5) +  
    geom_line(aes(y=med))+
    geom_point(aes(y=med))+
  #    geom_line(aes(y=highquart),color="blue", linetype="dotted")+
##      geom_line(aes(y=lowquart),color="blue", linetype="dotted")+
   #     geom_line(aes(y=ninefive),color="red", linetype="dotted")+
    #  geom_line(aes(y=five),color="red", linetype="dotted")+
  theme_bw()+
    labs(
      title = "",
      x = "",
      y = "")
plot
```

# output data
```{r}
DF=rbind(quantiles2,quantiles3,quantiles4,quantiles5,quantiles6,quantiles7,quantiles8)
write.csv(DF, here::here("output","quantile_overall.csv"))
```