---
title: "otmedia_appro_model"
author: "Billy"
date: "30/05/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '/workspace')
```


```{r}
library("dplyr")
library("tidyverse")
library("lubridate")
library("foreign")
library("nnet")
library("ggplot2")
library("VGAM")
library("bayesm")
library("finalfit")
library("here")
library("rms")
library("pROC")

```

```{r}
DF <- read_csv(here::here("output","otmedia_outcome.csv"))
DF <- DF %>% filter (age>3)
DF$outcome <- as.factor(DF$outcome)
DF$ethnicity_6 <- as.factor(DF$ethnicity_6)
DF$imd <- as.factor(DF$imd)
DF$region <- as.factor(DF$region)
DF$charlsonGrp <- as.factor(DF$charlsonGrp)
DF$ab12b4 <- as.factor(DF$ab12b4)
DF$outcome <- relevel(DF$outcome, ref = "1")
DF$ethnicity_6 <- relevel(DF$ethnicity_6, ref = "White")
DF$imd <- relevel(DF$imd, ref = "1")
DF$region <- relevel(DF$region, ref = "East")
DF$charlsonGrp <- relevel(DF$charlsonGrp, ref = "zero")
DF$ab12b4 <- relevel(DF$ab12b4, ref = "0")
DF <- DF %>% dplyr::select(outcome,age,sex,ethnicity_6,region,charlsonGrp,imd,ab12b4)
DF <- DF %>% filter (DF$sex=="M"|DF$sex=="F")
DF <- DF %>% filter (!is.na(outcome))
DF <- DF %>% filter (!is.na(ethnicity_6))
DF <- DF %>% filter (!is.na(imd))
DF <- DF %>% filter (!is.na(region))
DF <- DF %>% filter (!is.na(charlsonGrp))
DF <- DF %>% filter (!is.na(age))
DF <- DF %>% filter (!is.na(sex))
DF <- DF %>% filter (!is.na(ab12b4))
```

```{r}

# Data Partition 
set.seed(777)
ind <- sample(2,nrow(DF),
              replace = TRUE,
              prob = c(0.75,0.25))

training <- DF[ind==1,]
testing <- DF[ind==2,]

### use training dataset to develop the model
m1 <- vgam(outcome ~ rcs(age, knots = 5) + sex + ethnicity_6 + region + charlsonGrp + imd + ab12b4, family = multinomial(parallel = FALSE, refLevel = 1), data =training)

summaryvglm(m1)
```





```{r}
###relative risk ratio ###
exp(coefficients(m1,matrix=TRUE))
```

```{r}
m0.1 <- multinom(outcome ~ age + sex , data =training)
m0.2 <- multinom(outcome ~ rcs(age, knots = 5) + sex , data =training)
anova(m0.1, m0.2)
```


```{r}
### Table 1. Description and descriptive statistics for the case studies for each outcome category separately.
# columns for  table
colsfortab <- colnames(training)
training %>% summary_factorlist(explanatory = colsfortab) -> t1
t1
```

```{r}
testing %>% summary_factorlist(explanatory = colsfortab) -> t2
t2
```


### Parametric nominal calibration plot for the validation data of the ovarian tumor case study for each outcome category separately ((a)–(c)) and overall (d).

```{r}
outcome=testing$outcome
k=3
p <- predict(m1 , newdata = testing,type="response")
LP <- predict(m1, newdata = testing)
r=1
estimates=FALSE
dfr=2
plotoverall=TRUE
datapoints=TRUE
smoothing=TRUE
smoothpar=1
intercept=FALSE
slope=FALSE
test=FALSE
  # probabilities
  probs <- split(p,col(p))    
  
  # linear predictors necessary for non-parametric calibration plot - give a name to each linear predictor 
  # seperately
  lps <- split(LP,col(LP))
  for(i in 1:(k-1)){assign(paste("lp", i, sep = ""),unlist(lps[[i]]))}
aaa <- length(LP[,1])
bbb <- length(outcome)
cbind(aaa,bbb)
```


```{r}
  ###############################################
  # parametric logistic recalibration framework 
  # cf. section 2.2.1.                          
  ###############################################
  
  # reference category r
  # LP = matrix with linear predictors


  fitp<-vglm(outcome~LP,family=multinomial(refLevel=r))
  if(isTRUE(estimates)){est<-coefficients(fitp)
  names(est) <- paste('EST',names(est),sep='.')}
  
```





```{r}
  
  fitnp<-vgam(outcome~s(lp1,df=dfr)+s(lp2,df=dfr),family=multinomial(refLevel=r))
  
  
  ###############################################                  
  # Separate (non-)parametric calibration plots
  ###############################################
  
  
  par(mfrow=c(ceiling(k/2),2))
  for(i in 1:k){p <- unlist(probs[[i]])
  if(isTRUE(smoothing)){color<-'grey'}else{color<-1+i}
 
  matplot(p,fitted(fitp)[,i],type="p",pch=i,col=color,lwd=1,ylab="",xlab="",xlim=0:1,ylim=0:1)
  par(new=T)
  ref <- rbind(c(0,0),c(1,1))
  matplot(ref,ref,type="l",col=1,lwd=2,ylab="Observed proportions",xlab="Predicted probabilities",xlim=0:1,ylim=0:1)
  # smoother for calibration plots 
  ##################################
  # a = smoothing parameter
  if(isTRUE(smoothing)){
    a = smoothpar
    points(smooth.spline(p, fitted(fitp)[,i],spar=a), type="l", col=(1+i), lwd = 4)}
  # legend
  legende <- c(paste("outcome ", i, sep = ""))
  legend(x=0.6, y=(0.2),col=(1+i),lty =1,legend=legende)
  title(main = "Parametric calibration plot")
  par(new=F)} 
```


```{r}
  
  # non-parametric calibration plot 
  # cf. section 2.2.2.              
  ###################################
  
  par(mfrow=c(ceiling(k/2),2))
  for(i in 1:k){p <- unlist(probs[[i]])
  if(isTRUE(smoothing)){color<-'grey'}else{color<-1+i}
  plot2 <- matplot(p,fitted(fitnp)[,i],type="p",pch=i,col=color,lwd=1,ylab="",xlab="",xlim=0:1,ylim=0:1)
  par(new=T)
  ref <- rbind(c(0,0),c(1,1))
  matplot(ref,ref,type="l",col=1,lwd=2,ylab="Observed proportions",xlab="Predicted probabilities",xlim=0:1,ylim=0:1)
  # smoother for calibration plots 
  ##################################
  # a = smoothing parameter
  if(isTRUE(smoothing)){
    a = smoothpar
    points(smooth.spline(p, fitted(fitnp)[,i],spar=a), type="l", col=(1+i), lwd = 4)}
  # legend
  legende <- c(paste("cat ", i, sep = ""))
  legend(x=0.6, y=(0.2),col=(1+i),lty =1,legend=legende)
  title(main = "Non-parametric calibration plot")
  par(new=F)}
  
```



```{r}
  if(isTRUE(plotoverall)){
    
    
    # parametric calibration plot 
    # cf. section 2.2.2.          
    ###############################
    
    if(isTRUE(datapoints)){for(i in 1:k){p <- unlist(probs[[i]])
    plot3 <- matplot(p,fitted(fitp)[,i],type="p",pch=i,col=(1+i),lwd=1,ylab="",xlab="",xlim=0:1,ylim=0:1)
    par(new=T)}}
    ref <- rbind(c(0,0),c(1,1))
    matplot(ref,ref,type="l",col=1,lwd=2,ylab="Observed proportions",xlab="Predicted probabilities",xlim=0:1,ylim=0:1)
    # smoother for calibration plots 
    ##################################
    # a = smoothing parameter
    if(isTRUE(smoothing)){
      a = smoothpar
      for(i in 1:k){p <- unlist(probs[[i]])
      points(smooth.spline(p, fitted(fitp)[,i],spar=a), type="l", col=(1+i), lwd = 4)}}
    # legend
    for(i in 1:k){if(i <= 2){legende <- c("cat 1","cat 2")}
      if(i > 2){legende <- c(legende,paste("cat ", i, sep = ""))}}
    legend(x=0.7, y=(0.20+(k-3)*0.05),col=2:(k+1),lty =1,legend=legende)
    title(main = "Parametric calibration plot")
    par(new=F)
    
    # non-parametric calibration plot 
    # cf. section 2.2.2.              
    ###################################
    
    
    if(isTRUE(datapoints)){for(i in 1:k){p <- unlist(probs[[i]])
    plot4 <- matplot(p,fitted(fitnp)[,i],type="p",pch=i,col=(1+i),lwd=1,ylab="",xlab="",xlim=0:1,ylim=0:1)
    par(new=T)}}
    ref <- rbind(c(0,0),c(1,1))
    matplot(ref,ref,type="l",col=1,lwd=2,ylab="Observed proportions",xlab="Predicted  probabilities",xlim=0:1,ylim=0:1)
    # smoother for calibration plots 
    ##################################
    # a = smoothing parameter
    if(isTRUE(smoothing)){a = smoothpar
    for(i in 1:k){p <- unlist(probs[[i]])
    points(smooth.spline(p, fitted(fitnp)[,i],spar=a), type="l", col=(1+i), lwd = 4)}}
    # legend
    for(i in 1:k){if(i <= 2){legende <- c("cat 1","cat 2")}
      if(i > 2){legende <- c(legende,paste("cat ", i, sep = ""))}}
    legend(x=0.7, y=(0.20+(k-3)*0.05),col=2:(k+1),lty =1,legend=legende)
    title(main = "Non-parametric calibration plot")
    par(new=F)}
```


### Discrimination
### polytomous discrimination index  
```{r}
#Estimates of PDI and its components
testing$outcome <- as.numeric(testing$outcome)
p <- predict(m1 , newdata = testing,type="response")
df.p <- as.data.frame(p)
head(df.p)
data <- (cbind(testing$outcome,df.p))
```


```{r}
names(data) <- c("outcome","p1","p2","p3")
pdiest<-function(data){
  
  y<-data$outcome
  ymin<-min(y)
  ymax<-max(y)
  noutcome<-ymax-ymin
  p<-prod(table(y))
  pdi<-c()
  
  for (i in 1:(noutcome+1)){
    
    predprob<-data[,(i+1)]  #READ predicted probabilities for level i
    t0<-table(predprob,y)   #CALCULATE frequencies of predicted probabilities for level i by outcome
    
    dim1<-dim(t0)[1]
    dim2<-dim(t0)[2]
    t<-cbind(t0[,i],t0[,-i]) #REORDER columns
    restrictt<- if (noutcome == 1){matrix(t[,2:(noutcome+1)],ncol=1)} else {t[,2:(noutcome+1)] } #REMOVE first column of t
    
    c<-apply(restrictt,2,cumsum) #CALCULATE cumulative frequencies of predicted probabilities for level i by outcome
    cnew<- if (noutcome == 1) {rbind(rep(0,noutcome),matrix(c[1:(dim(c)[1]-1),],ncol=))} else {rbind(rep(0,noutcome),c[1:(dim(c)[1]-1),])} #INTRODUCE a row of zeros at the begining of c
    
    mat<-c()                     #MATRIX of 0s and 1s of dimension 2^(noutcome) x noutcome
    for (j in 1:noutcome){
      mat0<-cbind(mat,0)
      mat1<-cbind(mat,1)
      mat<-rbind(mat0,mat1)}
    
    r<-0
    for (k in 1:dim(mat)[1]){
      dt<-t(apply(restrictt, 1, function(x) mat[k,]*x))
      dcnew<-t(apply(cnew, 1, function(x) (1-mat[k,])*x))
      dfinal<-if (noutcome == 1) {cbind(t[,1],t(dt+dcnew))} else {cbind(t[,1],dt+dcnew)} #TAKE all combinations of frequencies and cumulative frequencies
      r<-r+sum(apply(dfinal,1,prod))/(1+sum(mat[k,]))}                                   #MULTIPLYIES across rows
    
    r<-r/p     #PDI component for outcome i
    pdi<-rbind(pdi,r)
  }
  pdi<-rbind(mean(pdi),pdi)
  pdi}

#Estimates and bootstrap 95% confidence intervals for PDI and its components
pdifunction<-function(data,nbs){
  #PDI estimate
  estimate<-pdiest(data)
  #BOOTSTRAP
  samplesize<-dim(data)[1]
  for (i in 1:nbs)
  {vec<-sample.int(samplesize,size=samplesize, replace=TRUE)
  mydatabs<-data[vec,]
  if (i<2) {pdibs<-pdiest(mydatabs)
  } else {
    pdibs<-cbind(pdibs,pdiest(mydatabs))
  }
  }
  
  stderr <- sqrt(apply(pdibs, 1, var))
  lowerci<- pmax(0, estimate - 1.96*stderr)
  upperci<- pmin(1, estimate + 1.96*stderr)
  
  estci<-cbind(estimate, lowerci, upperci)
  estci
}
```

```{r}
pdiest(data)
```
#Estimates and bootstrap 95% confidence intervals for PDI and its components
```{r}
pdifunction(data,5)
```




###"In one study's opinion, the pairwise approach is superior to the 1-versus-rest approach"
###"1-versus-rest approach"
###"1 vs rest"
```{r}
testing <- testing %>% 
  mutate(reoutcome1 = ifelse(outcome == 1 , 1, 0))
# Obtain the c statistic / AUC
c1 <- roc(testing$reoutcome1~df.p$`1`,ci=TRUE)
c1
```
# Plot the ROC curve

```{r}
plot(roc(testing$reoutcome1,df.p$`1`))
```

# "2 vs rest"
```{r}
testing <- testing %>% 
  mutate(reoutcome2 = ifelse(outcome == 2 , 1, 0))
# Obtain the c statistic / AUC
c1 <- roc(testing$reoutcome2~df.p$`2`,ci=TRUE)
c1
```

# Plot the ROC curve

```{r}
plot(roc(testing$reoutcome2,df.p$`2`))
```

# "3 vs rest"

```{r}
testing <- testing %>% 
  mutate(reoutcome3 = ifelse(outcome == 3 , 1, 0))
# Obtain the c statistic / AUC
c1 <- roc(testing$reoutcome3~df.p$`3`,ci=TRUE)
c1
```

# Plot the ROC curve

```{r}
plot(roc(testing$reoutcome3,df.p$`3`))
```


### "the pairwise approach "
#"1 vs 2"

```{r}
testing_1 <- testing %>% 
  filter(outcome ==1|outcome==2) %>% 
  mutate(reoutcome = ifelse(outcome == 1 , 1, 0))

order1 <- testing$outcome ==1|testing$outcome==2
df.p$reoutcome1<- df.p$`1`/(df.p$`1`+df.p$`2`)
df.p1 <- df.p[order1,]
# Obtain the c statistic / AUC
c1 <- roc(testing_1$reoutcome~df.p1$reoutcome1,ci=TRUE)
c1
```

# Plot the ROC curve
```{r}
plot(roc(testing_1$reoutcome,df.p1$reoutcome1))
```


#"1 vs 3"
```{r}
testing_2 <- testing %>% 
  filter(outcome ==1|outcome==3) %>% 
  mutate(reoutcome = ifelse(outcome == 1 , 1, 0))
order2 <- testing$outcome ==1|testing$outcome==3
df.p$reoutcome2 <- df.p$`1`/(df.p$`1`+df.p$`3`)
df.p2 <- df.p[order2,]

# Obtain the c statistic / AUC
c1 <- roc(testing_2$reoutcome~df.p2$reoutcome2,ci=TRUE)
c1
```

# Plot the ROC curve
```{r}
plot(roc(testing_2$reoutcome,df.p2$reoutcome2))
```


#"2 vs 3"
```{r}
testing_3 <- testing %>% 
  filter(outcome ==2|outcome==3) %>% 
  mutate(reoutcome = ifelse(outcome == 3 , 1, 0))
order3 <- testing$outcome ==2|testing$outcome==3
df.p$reoutcome3 <- df.p$`3`/(df.p$`2`+df.p$`3`)
df.p3 <- df.p[order3,]
# Obtain the c statistic / AUC
c1 <- roc(testing_3$reoutcome~df.p3$reoutcome3,ci=TRUE)
c1
```

# Plot the ROC curve
```{r}
plot(roc(testing_3$reoutcome,df.p3$reoutcome3))
```

  
  












