---
title: "Input Data Check"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r , include=FALSE}
require('tidyverse')
require("gtsummary")
require("ggplot2")
```

## cohort extractor
#### 1. study_population 

```{r }

dat=read_csv(here::here("output","input_general_population.csv"),
             col_types=cols_only(
               age=col_double(),
               sex=col_character()
             ))
dat %>%
  tbl_summary(
    statistic = list(
      all_continuous() ~ "{min}, {max}",
      all_categorical() ~ "{n} ({p}%)"))
rm(dat)
```

#### 2.1 study_population_covid_primary_care 
###### patient_index_date range
```{r}
dat=read_csv(here::here("output","input_covid_primarycare.csv"),
             col_types=cols_only(
               age=col_double(),
               sex=col_character(),
               patient_index_date=col_date()
             ))

range(dat$patient_index_date, na.rm=T)

dat$patient_index_date=ifelse(is.na(dat$patient_index_date),NA,1)

dat %>%
  tbl_summary(
    statistic = list(
      all_continuous() ~ "{min}, {max}",
      all_categorical() ~ "{n} ({p}%)"))
rm(dat)
```

#### 2.2 study_population_covid_SGSS
###### patient_index_date range
```{r}
dat=read_csv(here::here("output","input_covid_SGSS.csv"),
             col_types=cols_only(
               age=col_double(),
               sex=col_character(),
               patient_index_date=col_date()
             ))

range(dat$patient_index_date, na.rm=T)

dat$patient_index_date=ifelse(is.na(dat$patient_index_date),NA,1)

dat %>%
  tbl_summary(
    statistic = list(
      all_continuous() ~ "{min}, {max}",
      all_categorical() ~ "{n} ({p}%)"))
rm(list=ls())

```

#### 3. study_population_covid_admission
###### patient_index_date range
```{r}
dat=read_csv(here::here("output","input_covid_admission.csv"),
             col_types=cols_only(
               age=col_double(),
               sex=col_character(),
               patient_index_date=col_date()
             ))

range(dat$patient_index_date, na.rm=T)

dat$patient_index_date=ifelse(is.na(dat$patient_index_date),NA,1)

dat %>%
  tbl_summary(
    statistic = list(
      all_continuous() ~ "{min}, {max}",
      all_categorical() ~ "{n} ({p}%)"))
rm(list=ls())
```

#### 4.1 study_population_covid_death_ons
###### patient_index_date range
```{r}
dat=read_csv(here::here("output","input_covid_death_ons.csv"),
             col_types=cols_only(
               age=col_double(),
               sex=col_character(),
               patient_index_date=col_date()
             ))

range(dat$patient_index_date, na.rm=T)

dat$patient_index_date=ifelse(is.na(dat$patient_index_date),NA,1)

dat %>%
  tbl_summary(
    statistic = list(
      all_continuous() ~ "{min}, {max}",
      all_categorical() ~ "{n} ({p}%)"))
rm(list=ls())
```

#### 4.2 study_population_covid_death_cpns
###### patient_index_date range
```{r}
dat=read_csv(here::here("output","input_covid_death_cpns.csv"),
             col_types=cols_only(
               age=col_double(),
               sex=col_character(),
               patient_index_date=col_date()
             ))

range(dat$patient_index_date, na.rm=T)

dat$patient_index_date=ifelse(is.na(dat$patient_index_date),NA,1)

dat %>%
  tbl_summary(
    statistic = list(
      all_continuous() ~ "{min}, {max}",
      all_categorical() ~ "{n} ({p}%)"))
rm(list=ls())
```




##  process: data merging, select incident case
#### 1. covid infection: SGSS + primary care
###### patient_index_date range
```{r}
dat=read_csv(here::here("output","control_covid_infection.csv"),
             col_types=cols_only(
               age=col_double(),
               sex=col_character(),
               patient_index_date=col_date()
             ))

range(dat$patient_index_date, na.rm=T)

dat$patient_index_date=ifelse(is.na(dat$patient_index_date),NA,1)

dat %>%
  tbl_summary(
    statistic = list(
      all_continuous() ~ "{min}, {max}",
      all_categorical() ~ "{n} ({p}%)"))
rm(list=ls())
```


#### 2.1 covid hospital admission
###### patient_index_date range
```{r}
dat=read_csv(here::here("output","case_covid_admission.csv"),
             col_types=cols_only(
               age=col_double(),
               sex=col_character(),
               patient_index_date=col_date()
             ))

range(dat$patient_index_date, na.rm=T)

dat$patient_index_date=ifelse(is.na(dat$patient_index_date),NA,1)

dat %>%
  tbl_summary(
    statistic = list(
      all_continuous() ~ "{min}, {max}",
      all_categorical() ~ "{n} ({p}%)"))
rm(list=ls())
```

#### 2.2 covid hospital admission-control (remove worse_outrome_after)
###### patient_index_date range
```{r}
dat=read_csv(here::here("output","control_covid_admission.csv"),
             col_types=cols_only(
               age=col_double(),
               sex=col_character(),
               patient_index_date=col_date()
             ))

range(dat$patient_index_date, na.rm=T)

dat$patient_index_date=ifelse(is.na(dat$patient_index_date),NA,1)

dat %>%
  tbl_summary(
    statistic = list(
      all_continuous() ~ "{min}, {max}",
      all_categorical() ~ "{n} ({p}%)"))
rm(list=ls())
```


#### 3. covid death: ONS +CPNS
###### patient_index_date range
```{r}
dat=read_csv(here::here("output","case_covid_icu_death.csv"),
             col_types=cols_only(
               age=col_double(),
               sex=col_character(),
               patient_index_date=col_date()
             ))

range(dat$patient_index_date, na.rm=T)

dat$patient_index_date=ifelse(is.na(dat$patient_index_date),NA,1)

dat %>%
  tbl_summary(
    statistic = list(
      all_continuous() ~ "{min}, {max}",
      all_categorical() ~ "{n} ({p}%)"))
rm(list=ls())
```



##  after matching:
#### 1. outcome 2
###### patient_index_date range
```{r}
dat=read_csv(here::here("output","matched_combined_infection_hosp.csv"),
             col_types=cols_only(
               age=col_double(),
               sex=col_character(),
               patient_index_date=col_date()
             ))

range(dat$patient_index_date, na.rm=T)


dat %>%
  tbl_summary(
    statistic = list(
      all_continuous() ~ "{min}, {max}",
      all_categorical() ~ "{n} ({p}%)"))
rm(list=ls())
```

#### 2. outcome 3
###### patient_index_date range
```{r}
dat=read_csv(here::here("output","matched_combined_hosp_icu_death.csv"),
             col_types=cols_only(
               age=col_double(),
               sex=col_character(),
               patient_index_date=col_date()
             ))

range(dat$patient_index_date, na.rm=T)


dat %>%
  tbl_summary(
    statistic = list(
      all_continuous() ~ "{min}, {max}",
      all_categorical() ~ "{n} ({p}%)"))
rm(list=ls())
```




##  after extracting variables:
#### 1.1 outcome 2, case
###### patient_index_date range
```{r}
dat=read_csv(here::here("output","input_outcome_2_case.csv"),
             col_types=cols_only(
               age=col_double(),
               sex=col_character(),
               patient_index_date=col_date()
             ))

range(dat$patient_index_date, na.rm=T)


dat %>%
  tbl_summary(
    statistic = list(
      all_continuous() ~ "{min}, {max}",
      all_categorical() ~ "{n} ({p}%)"))
rm(list=ls())
```

#### 1.2 outcome 2, control
###### patient_index_date range
```{r}
dat=read_csv(here::here("output","input_outcome_2_control.csv"),
             col_types=cols_only(
               age=col_double(),
               sex=col_character(),
               patient_index_date=col_date()
             ))

range(dat$patient_index_date, na.rm=T)


dat %>%
  tbl_summary(
    statistic = list(
      all_continuous() ~ "{min}, {max}",
      all_categorical() ~ "{n} ({p}%)"))
rm(list=ls())
```




#### 2.1 outcome 3, case
###### patient_index_date range
```{r}
dat=read_csv(here::here("output","input_outcome_3_case.csv"),
             col_types=cols_only(
               age=col_double(),
               sex=col_character(),
               patient_index_date=col_date()
             ))

range(dat$patient_index_date, na.rm=T)


dat %>%
  tbl_summary(
    statistic = list(
      all_continuous() ~ "{min}, {max}",
      all_categorical() ~ "{n} ({p}%)"))
rm(list=ls())
```

#### 2.2 outcome 3, control
###### patient_index_date range
```{r}
dat=read_csv(here::here("output","input_outcome_3_control.csv"),
             col_types=cols_only(
               age=col_double(),
               sex=col_character(),
               patient_index_date=col_date()
             ))

range(dat$patient_index_date, na.rm=T)


dat %>%
  tbl_summary(
    statistic = list(
      all_continuous() ~ "{min}, {max}",
      all_categorical() ~ "{n} ({p}%)"))
rm(list=ls())
```





##  merging dataset & add variables
#### 1. outcome 2
###### patient_index_date range
```{r}
dat=read_csv(here::here("output","matched_outcome2.csv"),
             col_types=cols_only(
               age=col_double(),
               sex=col_character(),
               patient_index_date=col_date()
             ))

range(dat$patient_index_date, na.rm=T)


dat %>%
  tbl_summary(
    statistic = list(
      all_continuous() ~ "{min}, {max}",
      all_categorical() ~ "{n} ({p}%)"))
rm(list=ls())
```

#### 2. outcome 3
###### patient_index_date range
```{r}
dat=read_csv(here::here("output","matched_outcome3.csv"),
             col_types=cols_only(
               age=col_double(),
               sex=col_character(),
               patient_index_date=col_date()
             ))

range(dat$patient_index_date, na.rm=T)


dat %>%
  tbl_summary(
    statistic = list(
      all_continuous() ~ "{min}, {max}",
      all_categorical() ~ "{n} ({p}%)"))
rm(list=ls())
```
