---
title: "data flow numbers"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.table.format="html")
library('tidyverse')
library('dplyr')
library('lubridate')
library(magrittr)
library(Gmisc)
library(glue)
library(crayon)
library(grid)
```

```{r}
DF=data_frame()
```


# control
## covid infection- SGSS
```{r echo=FALSE, message=FALSE, warning=FALSE}
# impoprt data
df1 <- read_csv(here::here("output", "input_covid_SGSS.csv"))
df1=df1%>%filter(patient_index_date <= as.Date("2021-12-31"))
# filter SGSS (exclude SGSS+admission, SGSS+death)
df1 =df1%>%filter( !is.na(patient_index_date)) # SGSS case
round(nrow(df1)/5)*5

DF[1,1]=paste0("covid infection- SGSS")
DF[1,2]=paste0(round(nrow(df1)/5)*5)
```

## covid infection- SGSS - incident cases
```{r echo=FALSE, message=FALSE, warning=FALSE}
df1=df1%>%
  filter(is.na(primary_care_covid_date),
         is.na(covid_admission_date),
         is.na(died_date_cpns), 
         is.na(died_date_ons_covid))

round(nrow(df1)/5)*5


DF[2,1]=paste0("covid infection- SGSS - incident cases")
DF[2,2]=paste0(round(nrow(df1)/5)*5)
```

## covid infection- primary care
```{r echo=FALSE,message=FALSE, warning=FALSE}
df2<- read_csv(here::here("output", "input_covid_primarycare.csv"))
df2=df2%>%filter(patient_index_date <= as.Date("2021-12-31"))
df2 =df2%>%filter( !is.na(patient_index_date)) # primary care case
round(nrow(df2)/5)*5

DF[3,1]=paste0("covid infection- primary care")
DF[3,2]=paste0(round(nrow(df2)/5)*5)
```

## covid infection- primary care- incident cases
```{r echo=FALSE,message=FALSE, warning=FALSE}
df2=df2%>%
  filter(is.na(SGSS_positive_test_date),
         is.na(covid_admission_date),
         is.na(died_date_cpns), 
         is.na(died_date_ons_covid))
round(nrow(df2)/5)*5

DF[4,1]=paste0("covid infection- primary care- incident cases")
DF[4,2]=paste0(round(nrow(df2)/5)*5)

```

## covid infection - merged sgss & primary care
```{r echo=FALSE,message=FALSE, warning=FALSE}
df=rbind(df1,df2)
round(nrow(df)/5)*5



DF[5,1]=paste0("covid infection - merged sgss & primary care")
DF[5,2]=paste0(round(nrow(df)/5)*5)

```

## covid infection - aggregated sgss & primary care
```{r echo=FALSE,message=FALSE, warning=FALSE}
# keep earlist covid infection date
df=df%>%
  group_by(patient_id)%>%
  arrange(patient_id,patient_index_date)%>%
  distinct(patient_id, .keep_all = TRUE)
round(nrow(df)/5)*5


DF[6,1]=paste0("covid infection - aggregated sgss & primary care")
DF[6,2]=paste0(round(nrow(df)/5)*5)
```

## covid infection - removed death/hospital in one month
```{r echo=FALSE,message=FALSE, warning=FALSE}
# calendar month for matching
df$cal_YM=format(df$patient_index_date,"%Y-%m")

## Control - covid infection without any covid severe outcome within 1 month
df.0=df%>%
  filter(
          is.na(covid_admission_date_after),
          is.na(died_date_cpns_after),
          is.na(died_date_ons_covid_after))
round(nrow(df.0)/5)*5

DF[7,1]=paste0("covid infection - removed death/hospital in one month")
DF[7,2]=paste0(round(nrow(df.0)/5)*5)
```

# case

## hospital admission
```{r echo=FALSE,message=FALSE, warning=FALSE}
df.1 <- read_csv(here::here("output", "input_covid_admission.csv"))
df.1=df.1%>%filter(patient_index_date <= as.Date("2021-12-31"))
df.1 =df.1%>%filter( !is.na(patient_index_date)) # hospital patient
round(nrow(df.1)/5)*5


DF[8,1]=paste0("hospital admission")
DF[8,2]=paste0(round(nrow(df.1)/5)*5)


```

## hospital admission - incident cases( remove SGSS/primary care 1 month before index)
```{r echo=FALSE,message=FALSE, warning=FALSE}
df.1=df.1%>%filter(
         is.na(SGSS_positive_test_date_before),
         is.na(primary_care_covid_date_before), 
         is.na(died_date_cpns_before),
         is.na(died_date_ons_covid_before))
round(nrow(df.1)/5)*5
df.1$cal_YM=format(df.1$patient_index_date,"%Y-%m")

DF[9,1]=paste0("hospital admission")
DF[9,2]=paste0(round(nrow(df.1)/5)*5)
```


# cohort- combined
```{r echo=FALSE,message=FALSE, warning=FALSE}
df.0$case=0
df.1$case=1
df=rbind(df.1,df.0)
round(nrow(df)/5)*5

DF[10,1]=paste0("cohort- combined")
DF[10,2]=paste0(round(nrow(df)/5)*5)
```

# cohort- combined - keep 1 patient
```{r echo=FALSE,message=FALSE, warning=FALSE}
# keep earlist covid positive date
df=df%>%
  group_by(patient_id)%>%
  arrange(patient_id,patient_index_date)%>%
  distinct(patient_id, .keep_all = TRUE)
round(nrow(df)/5)*5

DF[11,1]=paste0("cohort- combined - keep 1 patient")
DF[11,2]=paste0(round(nrow(df)/5)*5)


```

# eligible controls
```{r echo=FALSE,message=FALSE, warning=FALSE}
df0=df%>%filter(case==0)
round(nrow(df0)/5)*5


DF[12,1]=paste0("eligible controls")
DF[12,2]=paste0(round(nrow(df0)/5)*5)
```

# eligible cases
```{r echo=FALSE,message=FALSE, warning=FALSE}
df1=df%>%filter(case==1)
round(nrow(df1)/5)*5

DF[13,1]=paste0("eligible cases")
DF[13,2]=paste0(round(nrow(df1)/5)*5)


write_csv(DF,here::here("output","check_process_1.csv"))
```

# all included patients
```{r}

df=df%>%distinct(patinet_id)
nrow(df)
round(nrow(df)/5)*5


```

