---
title: "Matching with replacement"
author: "YT Y"
date: "07/04/2022"
output: 
  html_document:
   toc: true
   toc_depth: 2
   toc_float:
     collapsed: false
     smooth_scorll: false
---

tutorials: https://cran.r-project.org/web/packages/MatchIt/vignettes/MatchIt.html 

```{r setup, include=FALSE}
library('tidyverse')
library('MatchIt')
library("ggplot2")
library(knitr)
library(dplyr)
library(kableExtra)
knitr::opts_chunk$set(echo = TRUE)
options(knitr.table.format="html")
```


```{r}
# import
#setwd('/Users/yayang/Documents/GitHub/amr-uom-brit/output')
setwd(here::here("output"))

df1=read_csv(here::here("output","case_covid_hosp.csv"))
df1$case=1
df2=read_csv(here::here("output","control_covid_infection.csv"))
df2$case=0

#df1=read_csv("/Users/yayang/Documents/GitHub/amr-uom-brit/output/case_covid_hosp.csv")
#df1$case=1
#df2=read_csv("/Users/yayang/Documents/GitHub/amr-uom-brit/output/control_covid_infection.csv")
#df2$case=0

df=rbind(df1,df2)

# case
count(df1)
#control
count(df2)
rm(df1,df2)
```

# Check Initial Imbalance
 1. indicator of good balance: Std ~0, eCDF( empirical cumulative density function)~0, variance ratios~1
 2. imbalance need to be eliminated
```{r}
# No matching; constructing a pre-match matchit object
m.out0 <- matchit(case ~ age + sex + stp + cal_YM , data = df,
                 method = NULL, distance = "glm")

summary(m.out0)
```


# Matching

## Exact matching
 methods from wjchulme
https://github.com/opensafely/booster-effectiveness/blob/256eae9691d36c0a2c586c9bb307eefb24586c32/analysis/design.R
https://github.com/opensafely/booster-effectiveness/blob/256eae9691d36c0a2c586c9bb307eefb24586c32/analysis/match_seqtrialcox.R

```{r}
# 1:1 NN PS matching w/o replacement

caliper_variables <- c(age = 5,NULL)

exact_variables <- c("sex","stp","cal_YM", NULL)

m.out1 <- matchit(case ~ age + sex + stp + cal_YM , data = df,
                 method = "nearest", distance = "glm", # these two options don't really do anything because we only want exact + caliper matching
                 exact = exact_variables,
                 caliper = caliper_variables, std.caliper=FALSE,
                 replace=TRUE, ratio=6)
m.out1


```


## Matching summary
Std Pair Dist.: average absolute within-pair difference of each covariate
When these values are small, better balance is typically achieved and estimated effects are more robust to misspecification of the outcome model (King and Nielsen 2019; Rubin 1973).
```{r}
# Checking balance after NN matching
summary(m.out1)
```


## Assessing the Quality of Matches
Points far from the solid diagonal line are the areas of the covariate distributions that differ between the treatment groups
```{r}
plot(m.out1, type = "jitter", interactive = FALSE)

plot(m.out1, type = "hist")

```


```{r}
plot(m.out1, type = "qq", interactive = FALSE,
     which.xs = c("age", "sex", "stp"))
```

```{r}
plot(summary(m.out1))
```

# output
```{r}

m.data1 <- get_matches(m.out1) # repeated id between sets(subclasses)
m.data1=m.data1%>%select("case","subclass","patient_id","patient_index_date","age","sex","stp","cal_YM","age_cat","region") # key variables for merging
write_rds(m.data1, here::here("output", "matched_patients.rds"))

m.data2 <- match.data(m.out1) # unique patient ID
m.data2=m.data2%>%select("patient_id","patient_index_date") 
write.csv(m.data2,here::here("output","matched_patients_id.csv"))

unmatched=subset(df, !df$patient_id %in% m.data1$patient_id)
unmatched=unmatched%>%filter(case==1)
write_rds(unmatched,here::here("output","unmatched_cases.rds"))


```


